\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Excellence: Expected Number}}
\begin{tasks}(3)
\task A factory makes components with a 1.2\% defect rate. In a shipment of 1250 components, what is the expected number of defective ones? Give your answer to the nearest whole number.
\task A basketball player's free throw percentage is 72.5\%. If they take 48 free throws in a season, how many are expected to be successful? Round to the nearest whole number.
\task In a multiple-choice test with 60 questions (5 options each), a student guesses all answers. What is the expected score? Would you be surprised if they got 20 correct? Explain.
\task A biased coin has P(Heads) = 0.42. If flipped 175 times, how many tails are expected? Give your answer to one decimal place.
\task A spinner has unequal sections: Red (30\%), Blue (25\%), Green (20\%), Yellow (25\%). If spun 240 times, how many times is it expected to land on Red or Green?
\task The probability of a customer making a purchase is 0.18. If 350 customers visit a store, what is the expected number of purchases? How does this help the store manager?
\task A dice is rolled 210 times. How many times is a number greater than 2 expected? What assumption are you making?
\task A bag contains 7 white, 4 black, and 9 red marbles. If a marble is drawn (with replacement) 180 times, how many times is a non-white marble expected?
\task A weather forecast says there's a 35\% chance of rain each day for the next 2 weeks (14 days). How many rainy days are expected? Would it be unusual to have only 2 rainy days? Explain.
\task A factory's quality control finds that 3 out of every 200 items are defective. In a production run of 8500 items, what is the expected number of defectives?
\task A student estimates they have a 65\% chance of passing each test. If they have 8 tests this term, how many are they expected to pass? What does this tell you about their likely overall performance?
\task A deck of cards: If you draw one card (with replacement) 156 times, how many times are you expected to draw a card that is NOT a heart?
\task A game gives a prize with probability \mbox{$\frac{1}{12}$}. If 144 people play, how many prizes are expected to be given out? The organiser has 15 prizes. Is this enough?
\task A survey suggests 22.5\% of teenagers own a tablet. In a school of 840 students, how many tablet owners are expected? Round appropriately.
\task A biased dice has P(6) = 0.25. If rolled 96 times, how many sixes are expected? If you actually got 30 sixes, would this be surprising?
\task A traffic light is green for 40 seconds, amber for 5, red for 25 in each cycle. If you approach it 90 times at random times, how many times are you expected to find it green?
\task A bag has marbles in ratio 3:5:2 (red:blue:green). If you draw (with replacement) 200 times, how many blue marbles are expected?
\task The chance of a flight being overbooked is 8\%. An airline has 225 flights next month. How many are expected to be overbooked? Why might the actual number differ?
\task A spinner has areas: A=40\%, B=30\%, C=20\%, D=10\%. If spun 150 times, how many times is it expected to land on B or C?
\task A factory finds that 0.8\% of its products fail within the first year. If it sells 12,500 products, how many failures are expected in the first year?
\end{tasks}

\end{document}