\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Foundation: Expected Number}}
\begin{tasks}(3)
\task The probability of rain tomorrow is 0.3. If you check the weather for 10 days, how many days are expected to have rain?
\task A coin is fair. If you flip it 20 times, how many heads are expected?
\task A dice is rolled 30 times. How many times is a 6 expected?
\task A bag has 3 red marbles and 7 blue marbles. If you draw one marble (and put it back) 50 times, how many red marbles are expected?
\task The probability of a bus being late is 0.1. If there are 40 buses, how many are expected to be late?
\task A spinner has 4 equal sections. If spun 24 times, how many times is section 1 expected?
\task A test has 5 multiple choice questions, each with 4 options. If guessing randomly, how many correct answers are expected?
\task A factory makes light bulbs. The probability of a bulb being faulty is 0.02. If they make 500 bulbs, how many faulty ones are expected?
\task A basketball player makes 60\% of free throws. If they take 25 shots, how many are expected to go in?
\task A deck of cards has 52 cards. If you draw one card (and replace it) 26 times, how many hearts are expected?
\task The probability of winning a game is 0.15. If you play 20 times, how many wins are expected?
\task A bag has 8 green balls and 2 yellow balls. If you draw one ball (and replace it) 30 times, how many yellow balls are expected?
\task A dice is rolled 18 times. How many times is an even number expected?
\task The chance of snow is 0.25. If you check for 12 days, how many snowy days are expected?
\task A coin is biased: P(Heads) = 0.4. If flipped 15 times, how many tails are expected?
\task A spinner has 5 equal sections. If spun 35 times, how many times is section 3 expected?
\end{tasks}

\end{document}