\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Proficient: Expected Number}}
\begin{tasks}(3)
\task The probability of a train being delayed is 0.15. In a year, there are 365 trains. Calculate the expected number of delayed trains.
\task A bag contains 4 red balls and 6 blue balls. If a ball is drawn and replaced 100 times, what is the expected number of times a blue ball will be drawn?
\task A factory produces 2,000 light bulbs. If the probability of a bulb being faulty is \mbox{$\frac{1}{200}$}, how many faulty bulbs are expected?
\task A student guesses on a 40-question multiple choice test (4 options each). What is the expected number of correct answers?
\task A basketball player makes \mbox{$\frac{3}{5}$} of their shots. If they take 75 shots in a tournament, how many are expected to go in?
\task The chance of a product being defective is 2.5\%. In a batch of 800 products, how many defectives are expected?
\task A dice is rolled 150 times. How many times is a prime number (2, 3, or 5) expected?
\task A survey shows 30\% of people prefer brand A. If you ask 250 people, how many are expected to prefer brand A?
\task A coin is biased with P(Heads) = 0.45. If flipped 80 times, how many tails are expected?
\task A spinner has sections: 40\% red, 25\% blue, 35\% green. If spun 120 times, how many times is it expected to land on blue?
\task The probability of a computer crashing in a day is 0.08. Over 50 days, how many crashes are expected?
\task A deck of cards: If you draw one card (with replacement) 130 times, how many face cards (J, Q, K) are expected?
\end{tasks}

\end{document}