\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\vspace*{0.4em}
{\LARGE \textbf{Excellence}}
\begin{tasks}(3)
\task {A student says this scale reads \mbox{$420$} g. Explain why they are wrong.\\[0.4em]
\hscale{0}{500}{7.5}{Mass scale}{g}}
\task {This measuring cylinder is marked every \mbox{$10$} mL with one halfway mark in between. What is the exact reading? Explain how you know.\\[0.4em]
\cylinder{Measuring cylinder}{100}{55}{mL}}
\task {This thermometer reading rises by \mbox{$15^\circ$}C. What will the new temperature be?\\[0.4em]
\thermo{Thermometer}{30}{-6}{$^\circ$C}}
\task {This speedometer needle moves \mbox{$12$} km/h faster. What will the new speed be?\\[0.4em]
\speedo{Speedometer}{100}{81}{km/h}}
\task {A charity target is \mbox{$500$}. The pointer is at \mbox{$350$}. How much more is needed?}
\task {A bag of flour should weigh \mbox{$425$} g. On a scale marked every \mbox{$50$} g, describe exactly where the pointer should be.}
\task {A measuring cylinder shows \mbox{$47.5$} mL. What must each small division be worth if the labels are every \mbox{$10$} mL?}
\task {A student reads a thermometer at \mbox{$-2^\circ$}C as positive \mbox{$2^\circ$}C. What sign have they ignored, and why does it matter?}
\task {Which is the larger jump: from \mbox{$35$} mL to \mbox{$60$} mL, or from \mbox{$-4^\circ$}C to \mbox{$8^\circ$}C?}
\task {A dial runs from \mbox{$0$} to \mbox{$100$} km/h in equal steps of \mbox{$20$}. What speed is one quarter of the way from \mbox{$60$} to \mbox{$80$}?}
\task {Explain why reading scales accurately depends on knowing the interval before looking at the pointer.}
\task {Create your own scale question using units, then write its answer.}
\end{tasks}

\end{document}
