\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Introduction to Circle Geometry --- Foundation}}
\begin{tasks}(3)
\task {Name the line from the centre of a circle to its edge.}
\task {Name the line right across a circle through the centre.}
\task {Name the curved part of the circumference between two points.}
\task {State the angle in a semicircle.}
\task {State the angle between a tangent and a radius at the point of contact.}
\task {If two angles stand on the same arc, how are they related?}
\task {If the angle at the centre is \mbox{$110^\circ$}, what is the angle at the circumference on the same arc?}
\task {If the angle at the circumference is \mbox{$42^\circ$}, what is the angle at the centre on the same arc?}
\task {An angle in a semicircle is labelled \mbox{$x$}. Find \mbox{$x$}.}
\task {An angle between a tangent and a radius is labelled \mbox{$x$}. Find \mbox{$x$}.}
\task {Two angles in the same segment are labelled \mbox{$58^\circ$} and \mbox{$x$}. Find \mbox{$x$}.}
\task {The angle at the centre is twice the angle at the circumference. If the circumference angle is \mbox{$37^\circ$}, find the centre angle.}
\task {Complete the fact: the angle at the centre is \mbox{$\underline{\hspace{1.8cm}}$} the angle at the circumference on the same arc.}
\task {Complete the fact: angles in the same segment are \mbox{$\underline{\hspace{1.8cm}}$}.}
\end{tasks}

\end{document}
