\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Excellence}}
\begin{tasks}(3)
\task A prism has a cross-section that is a right-angled triangle with legs 5 cm and 12 cm. If the prism is 30 cm long, calculate its volume.
\task A rectangular prism has a volume of 1.5 m\mbox{$^3$}. Its length is 2 m and its width is 0.75 m. Find its height in centimetres.
\task Two prisms have the same cross-sectional area. Prism A has depth 8 cm and volume 200 cm\mbox{$^3$}. Prism B has depth 12 cm. What is the volume of prism B?
\task A square prism and a rectangular prism have the same volume. The square prism has base side 6 cm and depth 10 cm. The rectangular prism has length 9 cm and width 5 cm. Find the height of the rectangular prism.
\task A triangular prism has a volume of 240 cm\mbox{$^3$}. The area of its triangular face is 20 cm\mbox{$^2$}. The prism is cut into two equal shorter prisms. What is the volume of each shorter prism?
\task A prism has a cross-section that is a trapezium with parallel sides 4 cm and 6 cm, and height 5 cm. If the prism is 15 cm long, find its volume.
\task A rectangular prism has dimensions in the ratio 2:3:5. Its volume is 810 cm\mbox{$^3$}. Find the actual dimensions.
\task A square prism has a volume that is 4 times the volume of a cube with side length 3 cm. If the square prism has depth 8 cm, find the side length of its base.
\task A triangular prism has a base triangle with area 18 cm\mbox{$^2$}. The prism is 25 cm long. If the prism is melted down and recast into a cube, what is the side length of the cube?
\task A prism has a cross-sectional area of 24 cm\mbox{$^2$}. Its volume is 360 cm\mbox{$^3$}. The prism is cut perpendicular to its length into three equal pieces. What is the volume of each piece?
\task A rectangular prism has a volume of 720 cm\mbox{$^3$}. Its length, width, and height are consecutive even numbers. Find the dimensions.
\task A square prism has a volume of 1000 cm\mbox{$^3$}. If its depth is increased by 20\% without changing the base, what is the new volume?
\task A triangular prism and a square prism have the same volume. The triangular prism has base area 16 cm\mbox{$^2$} and depth 15 cm. The square prism has base side length 4 cm. Find the depth of the square prism.
\task A prism has a cross-section that is a regular hexagon with area 54\mbox{$\sqrt{3}$} cm\mbox{$^2$}. If the prism is 20 cm long, calculate its volume.
\task A rectangular prism has length \mbox{$l$}, width \mbox{$w$}, and height \mbox{$h$}. If \mbox{$l = 2w$} and \mbox{$h = w + 2$}, and the volume is 192 cm\mbox{$^3$}, find the dimensions.
\task A square prism has a volume of 512 cm\mbox{$^3$}. If both the side length of the base and the depth are doubled, what is the new volume?
\task A triangular prism has a base triangle with sides 5 cm, 12 cm, and 13 cm (a right-angled triangle). If the prism is 18 cm long, find its volume.
\task A prism has a volume of 2.4 m\mbox{$^3$} and a depth of 1.2 m. The cross-section is a rectangle with length twice its width. Find the dimensions of the cross-section.
\task A square prism and a rectangular prism have equal depths. The square prism has base side 8 cm. The rectangular prism has base dimensions 10 cm by 6.4 cm. If their volumes are equal, find the common depth.
\task A prism has a cross-sectional area that varies along its length. The average cross-sectional area is 15 cm\mbox{$^2$} and the length is 40 cm. Estimate the volume of the prism.
\end{tasks}

\end{document}