\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Foundation}}
\begin{tasks}(3)
\task A rectangular prism has a base area of 12 cm\mbox{$^2$} and a depth of 5 cm. Find its volume.
\task A triangular prism has a triangular face area of 8 m\mbox{$^2$} and a length of 10 m. Calculate its volume.
\task The volume of a prism is 60 cm\mbox{$^3$} and its cross-sectional area is 15 cm\mbox{$^2$}. Find its depth.
\task A prism has a depth of 7 m and a volume of 84 m\mbox{$^3$}. What is the area of its face?
\task A square prism has a base side length of 3 cm and a depth of 8 cm. Find its volume.
\task A rectangular prism is 4 cm long, 5 cm wide, and 6 cm high. Calculate its volume.
\task A triangular prism has a triangular base with area 9 cm\mbox{$^2$} and a length of 12 cm. What is its volume?
\task The volume of a prism is 150 m\mbox{$^3$} and its depth is 6 m. Find the area of its cross-section.
\task A prism has a cross-sectional area of 20 cm\mbox{$^2$} and a volume of 100 cm\mbox{$^3$}. How long is it?
\task A hexagonal prism has a face area of 18 m\mbox{$^2$} and a depth of 5 m. Find its volume.
\task A rectangular prism has dimensions 2 m \mbox{$\times$} 3 m \mbox{$\times$} 4 m. Calculate its volume.
\task A prism has volume 72 cm\mbox{$^3$} and depth 9 cm. What is the area of its face?
\task A triangular prism has a base area of 14 cm\mbox{$^2$} and a length of 8 cm. Find its volume.
\task A square prism has volume 125 cm\mbox{$^3$} and depth 5 cm. Find the side length of its square base.
\task A rectangular prism has volume 240 cm\mbox{$^3$}, length 10 cm, and width 6 cm. Find its height.
\task A prism has a cross-sectional area of 25 m\mbox{$^2$} and a depth of 3 m. Calculate its volume.
\end{tasks}

\end{document}