\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Proficient}}
\begin{tasks}(3)
\task A chocolate bar is a triangular prism. The triangular end has a base of 4 cm and a height of 3 cm. The length of the bar is 20 cm. Calculate the volume of the chocolate bar in cm\mbox{$^3$}.
\task A hexagonal prism has a cross-sectional area of 25 m\mbox{$^2$}. If its volume is 300 m\mbox{$^3$}, what is the length of the prism?
\task A rectangular prism has a volume of 480 cm\mbox{$^3$}. Its length is 12 cm and its width is 5 cm. Find its height.
\task A triangular prism has a volume of 180 cm\mbox{$^3$}. The area of its triangular face is 15 cm\mbox{$^2$}. How long is the prism?
\task A square prism has a volume of 512 cm\mbox{$^3$} and a depth of 8 cm. Find the side length of its square base.
\task A prism has a cross-section that is a trapezium with area 18 cm\mbox{$^2$}. If the prism is 25 cm long, what is its volume?
\task A rectangular prism has dimensions 2.5 m by 3.2 m by 4.1 m. Calculate its volume to the nearest cubic metre.
\task A triangular prism has a base triangle with base 6 cm and height 4 cm. If the prism is 15 cm long, find its volume.
\task The volume of a prism is 1.2 m\mbox{$^3$} and its depth is 0.8 m. Find the area of its cross-section.
\task A prism has a cross-sectional area of 36 cm\mbox{$^2$} and a volume of 432 cm\mbox{$^3$}. What is its depth?
\task A rectangular prism has a volume of 960 cm\mbox{$^3$}. If its length is 16 cm and its height is 10 cm, find its width.
\task A square prism has a base side length of 7 cm and a volume of 441 cm\mbox{$^3$}. Find its depth.
\end{tasks}

\end{document}