\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Types of data — Excellence}}
\begin{tasks}(3)
\task A scientist collects plant growth data, then compares it to a published study. Identify both data types and explain the advantage of each.
\task Classify \mbox{`GPS coordinates'} as qualitative/quantitative and discrete/continuous, justifying your reasoning.
\task A market researcher uses both customer surveys and industry reports. Compare the data types and their strengths/weaknesses.
\task Explain why \mbox{`IQ score'} is considered discrete data despite measuring a continuous trait.
\task A hospital tracks patient recovery times (hours) and satisfaction ratings (1-5). Classify both variables fully.
\task Discuss whether \mbox{`time of day'} (e.g., 3:45 PM) is discrete or continuous, considering digital vs. analog measurement.
\task A student project uses school attendance records (secondary) and a new survey (primary). Explain the methodological implications.
\task Classify \mbox{`sound volume in decibels'} considering it can be measured continuously but recorded in whole numbers.
\task A company buys consumer spending data. Why might this be preferable to collecting their own primary data?
\task For climate research, would temperature data from weather stations be primary or secondary? Justify.
\task Explain how \mbox{`movie ratings (1-5 stars)'} can be considered both categorical and ordinal data.
\task A study uses \mbox{`reaction time in milliseconds'}. Classify and discuss measurement precision issues.
\task Compare primary vs. secondary data for a historical investigation vs. a scientific experiment.
\task Classify \mbox{`website click counts'} considering they're whole numbers but events occur continuously in time.
\task A researcher uses both lab measurements and published meta-analysis. Evaluate the data quality trade-offs.
\task Discuss: Is \mbox{`money in bank account'} discrete or continuous? Consider digital vs. physical currency.
\end{tasks}

\end{document}
