\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Types of data — Proficient}}
\begin{tasks}(3)
\task Classify \mbox{`distance travelled'} as qualitative/quantitative and discrete/continuous.
\task Classify \mbox{`blood type'} as qualitative/quantitative and discrete/continuous.
\task A student measures rainfall each day. Is this primary or secondary data?
\task A researcher uses government unemployment stats. Is this primary or secondary data?
\task Explain why \mbox{`number of siblings'} is discrete data.
\task Explain why \mbox{`height'} is continuous data.
\task Give an example of quantitative discrete data.
\task Give an example of quantitative continuous data.
\task Would measuring reaction times in an experiment give primary or secondary data?
\task Would analysing historical weather records give primary or secondary data?
\task Classify: \mbox{`time spent on homework'} (qualitative/quantitative, discrete/continuous).
\task Classify: \mbox{`favourite subject'} (qualitative/quantitative, discrete/continuous).
\task A company surveys its customers. What type of data source is this?
\task A journalist cites a published research paper. What type of data source is this?
\task Why might a researcher choose secondary data over primary data?
\task Why might primary data be more valuable than secondary data?
\end{tasks}

\end{document}
