\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Misleading graphs — Excellence}}
\begin{tasks}(3)
\task Critique the following graph description: A bar graph shows company profits over five years. The y-axis starts at 1 million dollars, and the bars are drawn as 3D cylinders. Identify at least three misleading aspects.
\task A pie chart shows market share of four companies. The slices are not labeled with percentages, and a 3D effect makes the front slice appear larger. How would you improve this chart?
\task A line graph shows population growth from 1950 to 2020. The y-axis uses a logarithmic scale but is not indicated. Explain why this is misleading.
\task Design a non-misleading bar graph for the following data: Product A: 150 units, Product B: 200 units, Product C: 180 units. Describe your choices of scale, labels, and title.
\task A graph uses a broken axis (zigzag) to omit zero. When is this acceptable? When is it misleading?
\task Compare two graphs of the same data: one with y-axis starting at 0, one with y-axis starting at the minimum data value. Discuss the visual impact.
\task A histogram has bins of unequal width. How would you adjust the presentation to avoid misinterpretation?
\task A scatter plot uses different sized circles to represent a third variable. Is this an effective or misleading technique? Justify.
\task Identify the misleading features in this description: A pictogram uses icons of different sizes to represent quantities, and the axis is not labeled.
\task A company presents a graph where the x-axis intervals are uneven (2000, 2005, 2020). Why is this misleading?
\task What are the five characteristics of a "good graph"? Explain each.
\task A graph shows a strong positive correlation, but the data points are few and the scale is exaggerated. How would you assess the validity of the conclusion?
\task You are given a misleading graph. List steps you would take to correct it.
\task True or False: A graph can be misleading even if all data is accurately plotted. Explain with an example.
\task A graph uses a secondary y-axis for a different unit. Discuss the potential for misinterpretation.
\task A bar graph uses horizontal bars with gradient shading that makes some bars appear darker and more prominent. Is this misleading? Why?
\end{tasks}

\end{document}
