\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Misleading graphs — Foundation}}
\begin{tasks}(3)
\task Which of the following is a characteristic of a good graph? (a) No title (b) Clearly labelled axes (c) Missing data points (d) Unlabelled axes
\task True or False: A graph with a y-axis that starts at 50 instead of 0 can be misleading.
\task Which graph is misleading? Graph A: y-axis starts at 0, bars proportional. Graph B: y-axis starts at 100, making small differences look large.
\task What is missing from a graph that has no title?
\task Which of these could make a graph misleading? (a) Using a 3D effect (b) Having a clear title (c) Labeling both axes (d) Using consistent scaling
\task True or False: A pie chart that uses 3D perspective can make some slices appear larger than they are.
\task Identify the misleading feature: A bar graph where the bars are drawn as cylinders, making the front cylinder appear larger.
\task Which graph correctly represents the data? Graph A: bars heights match numbers. Graph B: bars heights are doubled.
\task What should you check first when evaluating a graph? (a) Colors used (b) Whether axes are labelled (c) The font size (d) The paper size
\task True or False: A graph with no axis labels is still acceptable if the title explains everything.
\task Which of these is a good practice for graphs? (a) Start the y-axis at a high number to emphasize differences (b) Use a clear, descriptive title (c) Use as many colors as possible (d) Omit data points that don't fit
\task What is wrong with a graph that uses pictures instead of bars?
\task True or False: A line graph that omits zero on the y-axis is always misleading.
\task Which graph is more likely to be misleading? Graph A: y-axis has a break (zigzag) near zero. Graph B: y-axis is continuous from 0 to 100.
\end{tasks}

\end{document}
