\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Misleading graphs — Proficient}}
\begin{tasks}(3)
\task A bar graph shows sales for five products. The y-axis starts at 200 instead of 0. Why might this be misleading?
\task Describe two ways a pie chart can be misleading.
\task A line graph shows temperature over a week. The y-axis is truncated (starts at 15°C). How could this affect interpretation?
\task Which of the following graphs uses a misleading scale? Graph A: y-axis goes 0, 10, 20, 30. Graph B: y-axis goes 100, 110, 120, 130.
\task A company uses a pictogram where each icon represents 100 units, but the icons are drawn larger for higher numbers. Why is this misleading?
\task True or False: Using a 3D effect in a bar graph can make the bars appear larger than they are.
\task A graph has no title, but the axes are labelled "Time (months)" and "Profit (dollars)". What additional information should be included?
\task Which of these is a sign of a misleading graph? (a) Consistent spacing on axes (b) Clear labels (c) Missing zero on y-axis (d) Descriptive title
\task A graph shows two sets of data with different y-axis scales on the same plot. Why is this problematic?
\task A histogram uses unequal bin widths. Why might this be misleading?
\task What is the effect of using a logarithmic scale without indicating it?
\task A scatter plot uses different symbol sizes to represent a third variable. Is this misleading? Explain.
\end{tasks}

\end{document}
