¥documentclass[17pt,a4paper,landscape]{extarticle}
¥usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
¥usepackage{amsmath}
¥usepackage{amssymb}
¥usepackage{tasks}
¥usepackage{tikz}
¥usepackage{xcolor}
¥usepackage[sfdefault,lf]{FiraSans}
¥renewcommand{¥familydefault}{¥sfdefault}
¥setlength{¥parindent}{0pt}
¥pagestyle{empty}
¥settasks{label=¥textbf{¥arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
¥renewcommand{¥arraystretch}{1.15}
¥everymath{¥displaystyle}

¥begin{document}
¥sffamily
¥boldmath

¥boldmath

¥boldmath

¥boldmath

{¥LARGE ¥textbf{Regular/irregular polygon --- Excellence}}
¥begin{tasks}(3)
¥task {The sum of the interior angles of a polygon is ¥mbox{$(180n-360)^¥circ$}. Explain what the ¥mbox{$n$} represents.}
¥task {A polygon has interior-angle sum ¥mbox{$1620^¥circ$}. Find the number of sides.}
¥task {A regular polygon has each interior angle ¥mbox{$156^¥circ$}. Find the number of sides.}
¥task {A regular polygon has each interior angle ¥mbox{$165^¥circ$}. Find the number of sides.}
¥task {An irregular hexagon has five interior angles of ¥mbox{$118^¥circ$}, ¥mbox{$132^¥circ$}, ¥mbox{$147^¥circ$}, ¥mbox{$151^¥circ$}, and ¥mbox{$160^¥circ$}. Find the sixth angle.}
¥task {An irregular octagon has seven interior angles of ¥mbox{$120^¥circ$}, ¥mbox{$140^¥circ$}, ¥mbox{$150^¥circ$}, ¥mbox{$135^¥circ$}, ¥mbox{$160^¥circ$}, ¥mbox{$145^¥circ$}, and ¥mbox{$155^¥circ$}. Find the eighth angle.}
¥task {The interior angles of a regular polygon add to ¥mbox{$1980^¥circ$}. Find the polygon and one interior angle.}
¥task {A regular polygon has interior angles of ¥mbox{$140^¥circ$} each. Is this possible? Explain using the interior-angle formula.}
¥task {An irregular pentagon has angles in the ratio ¥mbox{$2:3:3:4:6$}. Find the five angles.}
¥task {An irregular hexagon has angles in the ratio ¥mbox{$3:4:5:5:6:7$}. Find the six angles.}
¥task {A regular polygon has one interior angle of ¥mbox{$x^¥circ$}. Write a formula for the sum of all interior angles in terms of ¥mbox{$x$} and the number of sides ¥mbox{$n$}.}
¥task {A student says, ``If all the angles in a polygon are equal, the polygon must be regular.'' Give a counterexample or explain why the claim is incomplete.}
¥task {A regular polygon has twice as many sides as a regular pentagon. Find its interior-angle sum and one interior angle.}
¥task {A polygon has ¥mbox{$10$} sides. Four interior angles are ¥mbox{$140^¥circ$}, three are ¥mbox{$150^¥circ$}, two are ¥mbox{$160^¥circ$}, and one angle is ¥mbox{$x^¥circ$}. Find ¥mbox{$x$}.}
¥task {A regular polygon has one interior angle that is ¥mbox{$24^¥circ$} more than the interior angle of a regular hexagon. Find the polygon.}
¥end{tasks}

¥end{document}
