\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Forming and solving equations from context — Foundation}}
\begin{tasks}(3)
\task Ben is \mbox{$x$} years old. His father is three times Ben's age minus 5 years. If the father is 40, form an equation and solve it to find Ben's age.
\task A rectangular field has a length of \mbox{$2x + 1$} and a width of \mbox{$x$}. If the perimeter is 32 m, form a simplified equation and find the width of the field.
\task Two cleaning companies charge the same. Company A charges a \textdollar 10 fee plus \textdollar 15 per hour, \mbox{$h$}. Company B charges a \textdollar 5 fee plus \textdollar 16 per hour. Form an equation and solve it to find the number of hours where the costs are equal.
\task Sarah has \mbox{$x$} marbles. Tom has 8 more than Sarah. Together they have 20 marbles. Form an equation and find how many marbles Sarah has.
\task A number \mbox{$n$} multiplied by 4 then added to 7 gives 31. Form an equation and solve for \mbox{$n$}.
\task The sum of three consecutive integers is 45. If the smallest is \mbox{$x$}, form an equation and find the integers.
\task A taxi charges \textdollar 3 per km plus a \textdollar 2 flagfall. If a ride costs \textdollar 17, form an equation and find the distance travelled.
\task A rectangle's length is 5 cm more than its width \mbox{$w$}. If the perimeter is 34 cm, form an equation and find the width.
\task Emma is twice as old as Liam. In 5 years, she will be 25. Form an equation and find Liam's current age.
\task A book costs \textdollar 8 more than a pen. If 2 books and 3 pens cost \textdollar 46, form an equation and find the cost of a pen.
\task The sum of a number and its double is 36. Form an equation and find the number.
\task A train travels at 80 km/h for \mbox{$t$} hours and covers 240 km. Form an equation and find the time taken.
\task A triangle has angles \mbox{$x$}, \mbox{$2x$}, and \mbox{$3x$}. Form an equation and find each angle.
\task A school has 120 students. There are 20 more girls than boys. If \mbox{$b$} is the number of boys, form an equation and find how many boys there are.
\end{tasks}

\end{document}