\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Forming and solving equations from context — Proficient}}
\begin{tasks}(3)
\task A shop sells pens for \textdollar 1.50 and pencils for \textdollar 0.80. Amy buys \mbox{$p$} pens and \mbox{$c$} pencils, spending \textdollar 9.40 in total. If she bought twice as many pencils as pens, form an equation and find how many pens she bought.
\task The area of a rectangle is 54 cm\textsuperscript{2}. Its length is 3 cm more than twice its width \mbox{$w$}. Form an equation and find the dimensions.
\task A car rental company charges \textdollar 40 per day plus \textdollar 0.15 per km. A customer's bill is \textdollar 85 for one day. Form an equation and find how many km were driven.
\task The sum of two numbers is 45. Their difference is 15. Form two equations and find the numbers.
\task A fraction has numerator \mbox{$n$} and denominator \mbox{$n+4$}. The fraction equals \mbox{$\frac{2}{3}$}. Form an equation and find the fraction.
\task A right-angled triangle has legs of length \mbox{$x$} and \mbox{$x+2$}. The hypotenuse is 10 cm. Form an equation and find \mbox{$x$}.
\task A concert ticket costs \textdollar 5 more for adults than for students. If 3 adult tickets and 5 student tickets cost \textdollar 155, form an equation and find the student ticket price.
\task A pool is being filled at 200 L/h. After \mbox{$t$} hours, there are 1200 L in the pool. Form an equation and find how long it has been filling.
\task The sum of the ages of a father and son is 50. In 10 years, the father will be twice as old as the son. Form equations and find their current ages.
\task A number is multiplied by 5, then 12 is subtracted. The result is the same as adding 8 to twice the number. Form an equation and find the number.
\task A rectangle's length is 7 cm longer than its width. If the perimeter is 46 cm, form an equation and find the area.
\task A mixture contains \mbox{$x$} L of 20\% juice and 5 L of 50\% juice. The final mixture is 35\% juice. Form an equation and find \mbox{$x$}.
\end{tasks}

\end{document}