\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\vspace*{0.4em}
{\LARGE \textbf{Excellence}}
\begin{tasks}(3)
\task {Use this tree for two coin tosses. A student says there are only \mbox{$3$} outcomes because the answers are heads, tails, or one of each. Are they correct? Explain.

\vspace{0.4em}
\twocointree}
\task {Use this tree to list the sample space for tossing a coin and rolling a die.

\vspace{0.4em}
\coindietree}
\task {Use the tree to say how many outcomes are in the sample space.

\vspace{0.4em}
\coindietree}
\task {Use the tree to find the probability of getting heads and a \mbox{$5$}.

\vspace{0.4em}
\coindietree}
\task {Use the tree to find the probability of getting tails and an even number.

\vspace{0.4em}
\coindietree}
\task {A student says the probability of drawing a red card from a standard deck is \mbox{$\frac{1}{4}$}. Are they correct? Explain.}
\task {A spinner has \mbox{$8$} equal sectors. \mbox{$3$} are red, \mbox{$3$} are blue, and \mbox{$2$} are yellow. What is the probability of not landing on yellow?}
\task {A bag contains \mbox{$2$} red, \mbox{$5$} blue, and \mbox{$3$} green counters. What is the probability of picking red or green?}
\task {A standard deck card is chosen. What is the probability of drawing a face card?}
\task {A standard deck card is chosen. What is the probability of drawing a red king?}
\end{tasks}

\end{document}
