\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\vspace*{0.4em}
{\LARGE \textbf{Proficient}}
\begin{tasks}(3)
\task {Use this tree to list the sample space for tossing two coins.

\vspace{0.4em}
\twocointree}
\task {Use the tree to say how many outcomes are in the sample space.

\vspace{0.4em}
\twocointree}
\task {Use the tree to write the probability of getting exactly one head.

\vspace{0.4em}
\twocointree}
\task {Use the tree to write the probability of getting two tails.

\vspace{0.4em}
\twocointree}
\task {A fair die is rolled. What is the probability of getting a factor of \mbox{$6$}?}
\task {A fair die is rolled. What is the probability of getting a multiple of \mbox{$3$}?}
\task {A spinner has \mbox{$5$} equal sectors labelled \mbox{$1,2,3,4,5$}. What is the probability of landing on a prime number?}
\task {A bag has \mbox{$8$} counters: \mbox{$3$} red, \mbox{$2$} blue, and \mbox{$3$} green. What is the probability of picking a blue counter?}
\task {A standard deck card is chosen. What is the probability that the card is a heart?}
\task {A standard deck card is chosen. What is the probability that the card is black?}
\task {Which is more likely: rolling a number greater than \mbox{$4$} on a die or picking a blue counter from a bag with \mbox{$1$} blue and \mbox{$3$} red counters?}
\task {Which is more likely: drawing a heart from a deck or getting heads on a fair coin?}
\end{tasks}

\end{document}
