\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\vspace*{0.4em}
{\LARGE \textbf{Excellence}}
\begin{tasks}(3)
\task {Use this tree for Questions 1--4.

\vspace{0.4em}\threecointree}
\task {Is the probability of at least one head equal to \mbox{$\frac{1}{2}$}? Explain.}
\task {Use the tree to find the probability of getting exactly two heads.}
\task {Use the tree to find the probability of getting at least one tail.}
\task {A student says HTH and THH are the same because both have two heads and one tail. Are they correct? Explain using tree paths.}
\task {Use this partial two-dice tree to help find the probability that the total is \mbox{$7$}.

\vspace{0.4em}\twodicetree}
\task {Use the tree to find the probability that both numbers are greater than \mbox{$4$}.}
\task {A spinner has equal sectors labelled A, B, and C. It is spun twice. What is the probability of getting exactly one A?}
\task {A spinner has equal sectors labelled \mbox{$1$}, \mbox{$2$}, \mbox{$3$}, and \mbox{$4$}. It is spun twice. What is the probability that both spins are even?}
\task {A bag has \mbox{$3$} red and \mbox{$2$} blue counters. A counter is picked, replaced, then picked again. What is the probability of getting one red and one blue in any order?}
\task {A bag has \mbox{$3$} red and \mbox{$2$} blue counters. A counter is picked, replaced, then picked again. What is the probability of getting two counters of the same colour?}
\task {Which is greater: the probability of exactly one head in three coin tosses or the probability of a total of \mbox{$7$} in two die rolls? Show enough working to justify.}
\task {Which is smaller: the probability of two blues from a bag with \mbox{$3$} red and \mbox{$2$} blue counters, with replacement, or the probability of two heads in two coin tosses? Explain.}
\task {Fill in the blank: when a fair coin is tossed three times, the probability of HHH is \mbox{$\frac{\square}{8}$}.}
\task {Fill in the blank: when a fair die is rolled twice, the probability of getting doubles is \mbox{$\frac{\square}{36}$}.}
\task {Which does not belong: outcome, branch, sample space, perimeter? Explain.}
\task {Explain why a full tree diagram helps avoid missing combined outcomes.}
\end{tasks}

\end{document}
