\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\vspace*{0.4em}
{\LARGE \textbf{Foundation}}
\begin{tasks}(3)
\task {Use this tree to list the possible outcomes for two fair coin tosses.

\vspace{0.4em}\twocointree}
\task {Use the tree to say how many outcomes are possible when two fair coins are tossed.

\vspace{0.4em}\twocointree}
\task {Use the tree to write the probability of getting HH.

\vspace{0.4em}\twocointree}
\task {Use the tree to write the probability of getting TT.

\vspace{0.4em}\twocointree}
\task {Use the tree to write the probability of getting exactly one head.

\vspace{0.4em}\twocointree}
\task {Use this tree for a coin toss and a fair die roll. How many outcomes are possible altogether?

\vspace{0.4em}\coindietree}
\task {Use the tree to find the probability of getting H and \mbox{$3$}.

\vspace{0.4em}\coindietree}
\task {Use the tree to find the probability of getting T and an even number.

\vspace{0.4em}\coindietree}
\task {Fill in the blank using the coin tree: the probability of at least one tail is \mbox{$\frac{\square}{4}$}.}
\task {Fill in the blank using the coin-and-die tree: the probability of heads is \mbox{$\frac{\square}{12}$}.}
\task {Which is more likely when two fair coins are tossed: two heads or exactly one head?}
\task {A student says there are only three outcomes when two coins are tossed: heads, tails, and one of each. Are they correct?}
\end{tasks}

\end{document}
