\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\vspace*{0.4em}
{\LARGE \textbf{Proficient}}
\begin{tasks}(3)
\task {Use this tree to list the full sample space for two fair coin tosses.

\vspace{0.4em}\twocointree}
\task {Use the tree to find the probability of getting exactly two heads.

\vspace{0.4em}\twocointree}
\task {Use the tree to find the probability of getting at least one head.

\vspace{0.4em}\twocointree}
\task {Use this tree for a spinner labelled \mbox{$1,2,3$} spun twice. List the outcomes where the total is \mbox{$4$}.

\vspace{0.4em}\threetwothreetree}
\task {Use the tree to find the probability that the total is \mbox{$4$}.

\vspace{0.4em}\threetwothreetree}
\task {A fair die is rolled twice. What is the probability of getting a \mbox{$6$} then an even number?}
\task {A fair die is rolled twice. What is the probability that both numbers are odd?}
\task {A bag has \mbox{$2$} red and \mbox{$1$} blue counter. A counter is picked, replaced, then picked again. What is the probability of red then blue?}
\task {A bag has \mbox{$2$} red and \mbox{$1$} blue counter. A counter is picked, replaced, then picked again. What is the probability of two blues?}
\task {A fair coin is tossed twice. What is the probability of getting the same result both times?}
\task {A fair coin is tossed twice. What is the probability of getting different results?}
\task {Fill in the blank: for two fair coin tosses, the probability of exactly one head is \mbox{$\frac{\square}{4}$}.}
\task {Fill in the blank: for two fair die rolls, the probability of getting two odd numbers is \mbox{$\frac{\square}{36}$}.}
\task {Which is greater: the probability of two heads in two coin tosses or the probability of a \mbox{$6$} then a \mbox{$6$} in two die rolls?}
\task {Which is smaller: the probability of red then blue from a red-blue spinner spun twice or the probability of two reds?}
\task {A student says the probability of H then \mbox{$5$} when a coin is tossed and a die is rolled is \mbox{$\frac{1}{6}$}. Are they correct?}
\task {Explain in one short sentence what a branch on a tree diagram shows.}
\end{tasks}

\end{document}
