\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Surface area — Foundation}}
\begin{tasks}(3)
\task A cube has side length 4 cm. Find its surface area.
\task A cube has side length 7 m. Find its surface area.
\task A rectangular prism is 8 cm long, 3 cm wide, and 2 cm high. Find its surface area.
\task A rectangular prism is 10 m long, 4 m wide, and 2 m high. Find its surface area.
\task Find the area of one square face of a cube with side length 6 cm.
\task A cube has 6 congruent faces. If one face has area 25 cm\mbox{$^2$}, what is the total surface area?
\task Find the area of the top and bottom faces together for a cuboid that is 9 cm by 5 cm by 4 cm.
\task Find the area of the four side faces together for a cuboid that is 9 cm by 5 cm by 4 cm.
\task A gift box is 12 cm long, 5 cm wide, and 3 cm high. How much cardboard is needed to make the closed box?
\task A fish tank is 40 cm long, 25 cm wide, and 30 cm high. Find the surface area of the glass if the tank has no lid.
\task A cube has surface area 54 cm\mbox{$^2$}. What is its side length?
\task A cuboid has length 6 cm, width 4 cm, and height 3 cm. Which pair of faces has the greatest area?
\task A closed cuboid has top and bottom area 48 cm\mbox{$^2$} in total and side-face area 56 cm\mbox{$^2$} in total. Find the surface area.
\task Explain in one sentence why surface area is measured in square units, not cubic units.
\end{tasks}

\end{document}
