\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Writing a statistical paragraph — Excellence}}
\begin{tasks}(3)
\task Analyse this weak paragraph: "Sports are good. 15 people like rugby. I play rugby too." Rewrite properly.
\task Given complex data (age vs. screen time correlation), write a sophisticated statistical paragraph.
\task How would statistical paragraphs differ for: a) business report, b) scientific paper, c) news article?
\task Write a paragraph comparing two data sets: School A (mean score 75) vs School B (mean score 68).
\task Critique: "The graph shows numbers. Some are big. This is interesting." How to improve?
\task Write a statistical paragraph that includes uncertainty: "Survey suggests 60-70% prefer option A."
\task How does writing style change when audience is: a) experts, b) general public, c) students?
\task Create a paragraph from multivariate data: Age, gender, and test score relationships.
\task Write a paragraph that addresses potential bias in data collection methods.
\task Compare statistical vs. narrative writing styles for presenting the same data.
\task Write a paragraph that leads to a specific recommendation based on the data.
\task How to handle contradictory evidence within a statistical paragraph?
\task Write a paragraph that connects local data (your school) to national statistics.
\task Design a rubric for assessing statistical paragraph quality.
\end{tasks}

\end{document}