\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Writing a statistical paragraph — Foundation}}
\begin{tasks}(3)
\task What are the three parts of a statistical paragraph?
\task Which part comes first: statistical statement, evidence, or context?
\task What should a statistical statement describe?
\task What should evidence sentences include?
\task What does context add to a statistical paragraph?
\task True or false: A statistical statement should include personal opinions.
\task True or false: Evidence should include numbers from the data.
\task True or false: Context explains why the data matters.
\task Write a statistical statement for: "Most students prefer pizza for lunch."
\task Write an evidence sentence using: "12 students chose pizza, 8 chose wraps."
\task Write a context sentence about lunch preferences at school.
\task Put in order: Evidence, Context, Statistical statement.
\task Improve this weak statement: "The graph goes up."
\task Circle which is a good statistical statement: "I like blue" / "Blue is the most common favourite colour".
\end{tasks}

\end{document}