\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Writing a statistical paragraph — Proficient}}
\begin{tasks}(3)
\task Given data: Favourite sports: Rugby 15, Netball 12, Basketball 8. Write a 3-sentence paragraph.
\task Data shows test scores: 60-69: 5 students, 70-79: 8, 80-89: 12. Write statistical statement and evidence.
\task Why is "The data shows a pattern" a weak statistical statement?
\task Improve: "Most people like chocolate ice cream because it's popular."
\task Write context for: "Students spend 2-3 hours daily on phones."
\task Compare these statements: A) "Maths is hard." B) "Most students find algebra challenging."
\task Data: Library visits per week: 0: 10, 1-2: 15, 3+: 5. Write full statistical paragraph.
\task What makes good evidence in a statistical paragraph?
\task Write a statistical statement about this trend: Temperature increases from winter to summer.
\task Add evidence to: "Reading time decreases as students get older."
\task Write context for weather data showing more rain in winter.
\task Critique this paragraph: "I think blue is best. 10 people chose it. Blue is nice."
\task Data: Mode of transport: Car 40%, Bus 30%, Walk 20%, Bike 10%. Write paragraph.
\task How does context differ from personal opinion?
\end{tasks}

\end{document}