\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Applying straight line graphs to solve problems — Excellence}}\\[0.2em]
Use straight-line models to compare options, find intersections, and justify decisions.

\begin{tasks}(3)
\task Gym Plan A has graph \mbox{$C=4v+10$}. Find the cost for \mbox{$8$} visits.

\task Gym Plan B has graph \mbox{$C=2v+26$}. Find the cost for \mbox{$8$} visits.

\task Using Gym Plan A and Gym Plan B, which plan is cheaper for \mbox{$3$} visits?

\task Using Gym Plan A and Gym Plan B, which plan is cheaper for \mbox{$10$} visits?

\task Solve \mbox{$4v+10=2v+26$} to find the number of visits where the two gym graphs intersect.

\task Explain what the intersection of the two gym graphs means in this context.

\task A tank empties with rule \mbox{$V=48-4t$}. Find the water volume after \mbox{$7$} minutes.

\task Using \mbox{$V=48-4t$}, find when the tank reaches \mbox{$12$} L.

\task A heating graph is \mbox{$T=5m+10$}. Find when the temperature reaches \mbox{$55^{\circ}\!\mathrm{C}$}.

\task A van trip has graph \mbox{$C=6k+12$}. Another has graph \mbox{$C=8k+4$}. Find both costs for \mbox{$5$} km.

\task Solve \mbox{$6k+12=8k+4$} to find where the two van-cost graphs intersect.

\task For short trips, which van option is cheaper? Use the intersection to justify your answer.

\task A snow-depth graph is \mbox{$d=4h+6$}. Find how long it takes for the depth to reach \mbox{$30$} cm.

\task A student says the graph \mbox{$C=3p+12$} is always more expensive than \mbox{$C=5p+4$}. Is the student correct? Use values or an equation to justify your answer.
\end{tasks}

\end{document}
