\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Applying straight line graphs to solve problems — Foundation}}\\[0.2em]
Use the straight-line rule or table to answer each question.

\begin{tasks}(3)
\task A movie ticket graph has rule \mbox{$C=5n+2$}, where \mbox{$n$} is the number of tickets. Find the cost when \mbox{$n=4$}.

\task A taxi fare graph has rule \mbox{$F=2d+6$}, where \mbox{$d$} is distance in km. Find the fare for \mbox{$7$} km.

\task A savings graph has rule \mbox{$S=10w+5$}, where \mbox{$w$} is weeks. How much is saved after \mbox{$6$} weeks?

\task A candle height graph has rule \mbox{$h=16-2t$}, where \mbox{$t$} is time in hours. Find the height after \mbox{$3$} hours.

\task A water tank graph has rule \mbox{$V=2t+3$}, where \mbox{$t$} is time in minutes. Find the water volume after \mbox{$8$} minutes.

\task A walking graph has rule \mbox{$d=0.4t+0.5$}, where \mbox{$t$} is time in minutes. Find the distance after \mbox{$5$} minutes.

\task For the graph \mbox{$C=5n+2$}, what does the \mbox{$+2$} mean in the context of movie tickets?

\task For the graph \mbox{$F=2d+6$}, what does the gradient \mbox{$2$} mean in the context of the taxi fare?

\task The rule for a plant graph is \mbox{$h=3w+10$}. What is the starting height of the plant?

\task The graph rule is \mbox{$B=92-8t$}, where \mbox{$B$} is battery percentage. How much battery is left after \mbox{$4$} hours?

\task The graph rule is \mbox{$h=30-3t$}, where \mbox{$h$} is water height in cm. After how many hours will the height be \mbox{$18$} cm?

\task The graph rule is \mbox{$C=4t+8$}, where \mbox{$t$} is bike-hire time in hours. How much does \mbox{$5$} hours cost?
\end{tasks}

\end{document}
