\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Applying straight line graphs to solve problems — Proficient}}\\[0.2em]
Use straight-line rules to interpret, predict, and solve context problems.

\begin{tasks}(3)
\task A bike-hire graph has rule \mbox{$C=4t+8$}. Find the cost for \mbox{$6$} hours, then state the fixed charge.

\task A phone battery graph has rule \mbox{$B=92-8t$}. Find the battery percentage after \mbox{$7$} hours.

\task A plant growth graph has rule \mbox{$h=3w+10$}. In which week will the plant reach \mbox{$25$} cm?

\task A tank drains according to \mbox{$V=30-3t$}. Find when the tank will be empty.

\task Courier A has graph \mbox{$C=5p+4$}, where \mbox{$p$} is the number of parcels. Find the cost for \mbox{$6$} parcels.

\task Courier B has graph \mbox{$C=3p+12$}. Find the cost for \mbox{$6$} parcels.

\task Using Courier A and Courier B, which company is cheaper for \mbox{$2$} parcels? Show the two costs.

\task Using Courier A and Courier B, which company is cheaper for \mbox{$8$} parcels? Show the two costs.

\task A temperature graph is \mbox{$T=5m+10$}, where \mbox{$m$} is minutes. Find the temperature after \mbox{$9$} minutes.

\task A snow-depth graph is \mbox{$d=4h+6$}. Find the depth after \mbox{$5$} hours, then explain what the \mbox{$+6$} means.

\task A school van trip costs \mbox{$C=6k+12$}, where \mbox{$k$} is distance in km. Find the total cost for \mbox{$9$} km.

\task A different van trip costs \mbox{$C=8k+4$}. Compare the two van costs for \mbox{$4$} km and decide which is cheaper.
\end{tasks}

\end{document}
