\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Using trig functions to calculate lengths of a right-angled triangle --- Excellence}}
\begin{tasks}(3)
\task A ladder makes an angle of \mbox{$72^\circ$} with the ground. The foot is 2.8 m from the wall. Find the ladder length and the height reached, both to 1 d.p.
\task A tower is 35 m away. The angle of elevation to the top is \mbox{$27^\circ$}. Find the tower height to 1 d.p.
\task A road rises at \mbox{$14^\circ$} for 120 m along the slope. Find the vertical rise and the horizontal distance, each to 1 d.p.
\task A boat is 50 m from a cliff. The angle of elevation to the top is \mbox{$38^\circ$}. Find the cliff height to 1 d.p.
\task A 9 m slide makes an angle of \mbox{$41^\circ$} with the ground. Find the platform height and the ground distance, both to 1 d.p.
\task A support wire is 18 m long and makes an angle of \mbox{$67^\circ$} with the ground. Find the mast height to 1 d.p.
\task From the top of a 12 m building, the angle of depression to a point on the ground is \mbox{$53^\circ$}. Find the distance from the base to the point, to 1 d.p.
\task A ramp rises 1.2 m and makes an angle of \mbox{$8^\circ$} with the ground. Find the ramp length to 2 d.p.
\task A kite string is 30 m long. The kite is 19 m high. Find the angle with the ground, then the horizontal distance to 1 d.p.
\task A tree is viewed from 14 m away at an angle of elevation of \mbox{$61^\circ$}. Move 6 m further back. Find the new angle to the nearest degree.
\task Angle \mbox{$36^\circ$}, adjacent 11 cm. Find the opposite side and the hypotenuse, both to 1 d.p.
\task Angle \mbox{$57^\circ$}, opposite 8.4 m. Find the adjacent side and the hypotenuse, both to 1 d.p.
\task A pole is viewed at \mbox{$48^\circ$}. Walk 7 m closer and the angle becomes \mbox{$62^\circ$}. Find the pole height to 1 d.p.
\task A cable is 26 m long and makes an angle of \mbox{$59^\circ$} with the ground. Move the anchor 4 m further away. Find the new cable length to 1 d.p.
\end{tasks}

\end{document}
