\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath
{\LARGE \textbf{Angles around a point --- Excellence}}
\begin{tasks}(3)
\task {Angles around a point are \mbox{$2x+10^\circ$}, \mbox{$x$}, and \mbox{$140^\circ$}. Find \mbox{$x$} and justify your method.}
\task {Angles around a point are \mbox{$3x$}, \mbox{$x+20^\circ$}, and \mbox{$100^\circ$}. Find \mbox{$x$} and all three angles.}
\task {Angles around a point are \mbox{$x$}, \mbox{$x+30^\circ$}, \mbox{$2x$}, and \mbox{$90^\circ$}. Find \mbox{$x$}.}
\task {Angles around a point are \mbox{$2x-10^\circ$}, \mbox{$x$}, \mbox{$x+20^\circ$}, and \mbox{$110^\circ$}. Find \mbox{$x$} and all four angles.}
\task {Three angles around a point are in the ratio \mbox{$3:5:7$}. Find the largest angle.}
\task {Four angles around a point are in the ratio \mbox{$2:3:4:9$}. Find all four angles.}
\task {One angle is twice another. A third angle is \mbox{$40^\circ$} more than the smaller angle. The three angles make a full turn. Find all three angles.}
\task {Two equal angles and one reflex angle make a full turn. The reflex angle is \mbox{$210^\circ$}. Find each equal angle.}
\task {Angles around a point are \mbox{$x$}, \mbox{$x+25^\circ$}, \mbox{$x+55^\circ$}, and \mbox{$2x$}. Find \mbox{$x$}.}
\task {A student says: if one angle is \mbox{$220^\circ$}, the other two equal angles must each be \mbox{$80^\circ$}. Explain the mistake and give the correct angles.}
\task {A point is split into six equal angles. Another point is split into four equal angles. Find the difference between one angle from the first point and one angle from the second point.}
\task {Four angles around a point are \mbox{$78^\circ$}, \mbox{$x$}, \mbox{$x$}, and \mbox{$x+24^\circ$}. Find \mbox{$x$}.}
\task {Three angles around a point are consecutive multiples of \mbox{$15^\circ$}. Their total is a full turn. Find the three angles.}
\task {A full turn is divided into three angles. The second angle is \mbox{$35^\circ$} more than the first. The third angle is twice the first. Find all three angles.}
\task {Explain why any claim that the angles around a point total more than \mbox{$360^\circ$} must be wrong if the angles do not overlap.}
\task {Create your own set of four different angles around a point that total \mbox{$360^\circ$}. One must be reflex.}
\end{tasks}
\end{document}
