\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath
{\LARGE \textbf{Transformation (Translation, reflection, enlargement) — Excellence}}\\[0.15em]
{\large Work carefully. Give complete reasons using coordinates, equal distances, vectors, and scale factors.}
\begin{tasks}(3)
\task $A$ is translated by $\begin{pmatrix}3\\2\end{pmatrix}$. Write the coordinates of the image of each vertex: $(-2,-1),(-1,-1),(-1,1),(-2,0)$. 

\task A triangle with vertices \mbox{$(-2,-1),(0,-1),(-1,1)$} is reflected in the line \mbox{$x=1$}. Write the image coordinates.

\task A shape is enlarged from centre \mbox{$(0,0)$} by scale factor \mbox{$2$}. Find the image of the points \mbox{$(-1,-1),(1,-1),(0,2)$}.

\task A shape is enlarged from centre \mbox{$(0,0)$} by scale factor \mbox{$\tfrac12$}. Find the image of the points \mbox{$(-2,-2),(2,-2),(0,4)$}.

\task Explain why a translation always keeps side lengths and angles the same.

\task Explain why a reflection changes orientation but keeps side lengths the same.

\task A rectangle has vertices \mbox{$(-3,-1),(-1,-1),(-1,1),(-3,1)$}. Describe a single translation that maps it to the rectangle with vertices \mbox{$(1,2),(3,2),(3,4),(1,4)$}.

\task A triangle has vertices \mbox{$(-2,1),(-1,3),(0,1)$}. It is reflected in the line \mbox{$y=0$}. Write the image coordinates and state what stays the same.

\task A shape and its image are similar. One side changes from \mbox{$3\text{ cm}$} to \mbox{$7.5\text{ cm}$}. Find the enlargement scale factor.

\task A shape is enlarged by scale factor \mbox{$3$} from centre \mbox{$(0,0)$}. The point \mbox{$(2,-1)$} is on the shape. Find its image.

\task A shape is enlarged by scale factor \mbox{$\tfrac12$} from centre \mbox{$(0,0)$}. The point \mbox{$(-4,6)$} is on the shape. Find its image.

\task A point moves by the vector $\begin{pmatrix}-5\\3\end{pmatrix}$. If it started at $(4,-2)$, where does it finish?

\task The point \mbox{$P(2,3)$} is reflected in the \mbox{$y$}-axis. Write the new coordinates and explain the change.

\task The point \mbox{$Q(-4,1)$} is reflected in the \mbox{$x$}-axis. Write the new coordinates and explain the change.

\task Which single transformation is impossible to describe fully without extra information: translation, reflection, or enlargement? Explain why.

\task Compare translation, reflection, and enlargement. Which preserve congruence, and which only preserve similarity?
\end{tasks}
\end{document}
