\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath
{\LARGE \textbf{Transformation (Translation, reflection, enlargement) — Foundation}}\\[0.15em]
{\large Use simple transformation words and complete descriptions.}
\begin{tasks}(3)
\task Point \mbox{$A(1,2)$} moves to \mbox{$A'(4,2)$}. Is this a translation, reflection, or enlargement?
\task Point \mbox{$B(-2,3)$} moves to \mbox{$B'(-2,-3)$}. Name the transformation.
\task Point \mbox{$C(2,1)$} moves to \mbox{$C'(4,2)$} from centre \mbox{$(0,0)$}. Is this an enlargement? If yes, give the scale factor.
\task A shape moves 5 units right and 2 units up. Write the translation vector.
\task A point at \mbox{$(3,-1)$} is reflected in the \mbox{$y$}-axis. Write the new coordinates.
\task A point at \mbox{$(-4,2)$} is reflected in the \mbox{$x$}-axis. Write the new coordinates.
\task A square is enlarged from side length \mbox{$2$} cm to side length \mbox{$6$} cm. Find the scale factor.
\task A triangle is enlarged from side length \mbox{$8$} cm to side length \mbox{$4$} cm. Find the scale factor.
\task Point $P(-1,4)$ is translated by $\begin{pmatrix}3\\-2\end{pmatrix}$. Write the image coordinates.
\task Point $Q(5,-2)$ is translated by $\begin{pmatrix}-4\\1\end{pmatrix}$. Write the image coordinates.
\task Shape \mbox{$A$} is reflected in the line \mbox{$x=0$}. What is another name for this line?
\task Shape \mbox{$B$} is reflected in the line \mbox{$y=0$}. What is another name for this line?
\end{tasks}
\end{document}
