\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Sampling variation --- Excellence}}
\begin{tasks}(3)
\task Three random samples estimate the proportion of students who own a laptop: \mbox{$11/30$}, \mbox{$37/100$}, \mbox{$381/1000$}. Which estimate would you report first, and why?
\task A student says, ``If a sample is random, every sample should give the same result.'' Explain carefully why this is false.
\task Two schools run polls on the same issue. School A uses repeated random samples of \mbox{$30$}. School B uses repeated random samples of \mbox{$1000$}. Compare the likely spread of their sample proportions.
\task A survey result from \mbox{$30$} people is used in a newspaper headline as if it represents the whole city exactly. Write one criticism using the idea of sampling variation.
\task A random sample of \mbox{$100$} gives \mbox{$48\%$} support. A random sample of \mbox{$1000$} gives \mbox{$51\%$} support. Which one should carry more weight when estimating the population value? Explain.
\task Explain why a larger sample size does not remove sampling variation completely.
\task A sample of \mbox{$30$} gives \mbox{$80\%$} support, but three later samples of \mbox{$1000$} give \mbox{$52\%$}, \mbox{$49\%$}, and \mbox{$51\%$}. Which result is more believable for the population, and why?
\task A researcher gets these percentages for the same question from repeated random samples: \mbox{$44\%, 61\%, 47\%, 55\%, 52\%$}. What do these changing results suggest about sampling variation?
\task Another researcher gets \mbox{$49\%, 50\%, 51\%, 50\%, 49\%$}. What does this suggest about their sample size compared with the first researcher?
\task Explain the difference between sampling variation and bias.
\task A sample of \mbox{$1000$} and a sample of \mbox{$30$} both come from the same population. Which sample is more likely to give an estimate close to the true population proportion? Justify your answer without saying ``because it is bigger'' only.
\task Write a short statistical statement comparing how sample sizes of \mbox{$30$}, \mbox{$100$}, and \mbox{$1000$} affect sampling variation.
\end{tasks}

\end{document}
