\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Sampling variation --- Foundation}}
\begin{tasks}(3)
\task What does sampling variation mean?
\task Two random samples from the same population give slightly different results. What idea does this show?
\task If you ask 30 students their favourite sport, will another random sample of 30 students always give exactly the same percentages?
\task Circle the larger sample size: \mbox{$30$}, \mbox{$100$}, \mbox{$1000$}.
\task Which sample size usually gives the most stable results: \mbox{$30$}, \mbox{$100$}, or \mbox{$1000$}?
\task Which sample size usually has the most sampling variation: \mbox{$30$}, \mbox{$100$}, or \mbox{$1000$}?
\task A random sample of \mbox{$30$} students has \mbox{$18$} who walk to school. Write this as a proportion.
\task A second random sample of \mbox{$30$} students has \mbox{$15$} who walk to school. Do the two samples have the same result?
\task A sample of \mbox{$100$} students gives \mbox{$42\%$} choosing soccer. Another sample of \mbox{$100$} gives \mbox{$39\%$}. Is this possible because of sampling variation?
\task A sample of \mbox{$1000$} voters gives \mbox{$51\%$} support. Another sample of \mbox{$1000$} gives \mbox{$50\%$} support. Is a small difference like this surprising?
\task Complete: Bigger samples usually have \rule{2cm}{0.4pt} sampling variation.
\task Complete: Smaller samples usually have \rule{2cm}{0.4pt} sampling variation.
\task Why is a sample of \mbox{$1000$} usually more reliable than a sample of \mbox{$30$}?
\task Give one reason why two fair random samples can still give different results.
\end{tasks}

\end{document}
