\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Sampling variation --- Proficient}}
\begin{tasks}(3)
\task A school surveys two random samples of \mbox{$30$} students about owning a bike. Sample A gives \mbox{$40\%$}. Sample B gives \mbox{$53\%$}. Explain why both results could still be reasonable.
\task Two random samples of \mbox{$100$} students are asked if they have a part-time job. One sample gives \mbox{$18\%$}, the other gives \mbox{$21\%$}. What does this suggest about sampling variation for samples of \mbox{$100$}?
\task Two random samples of \mbox{$1000$} students are asked if they bring lunch from home. One sample gives \mbox{$64\%$}, the other gives \mbox{$65\%$}. Why are the results closer together?
\task Put these sample sizes in order from most expected sampling variation to least: \mbox{$30$}, \mbox{$100$}, \mbox{$1000$}.
\task A true population proportion is close to \mbox{$50\%$}. Which sample size would you trust more for an estimate: \mbox{$30$} or \mbox{$1000$}? Give a reason.
\task A class claims, ``Our first sample gave \mbox{$70\%$}, so the population must be exactly \mbox{$70\%$}.'' Explain why this is poor reasoning.
\task Sample A of size \mbox{$30$} gives \mbox{$12$} students preferring basketball. Sample B of size \mbox{$100$} gives \mbox{$38$} students preferring basketball. Which sample gives the stronger estimate of the population proportion? Why?
\task A council takes three random samples on support for a new park: \mbox{$17/30$}, \mbox{$56/100$}, \mbox{$548/1000$}. Which result would you expect to be closest to the true population proportion?
\task Explain why increasing sample size usually reduces sampling variation, even when the sampling method stays random.
\task A poll of \mbox{$30$} people shows \mbox{$60\%$} support. Another poll of \mbox{$30$} shows \mbox{$43\%$} support. Should we be more worried about bias or accept that this might happen with small samples? Explain briefly.
\task A poll of \mbox{$1000$} people shows \mbox{$49\%$} support and another poll of \mbox{$1000$} shows \mbox{$62\%$} support. Does this large difference suggest sampling variation alone, or should you question the sampling process? Explain.
\task Write one sentence comparing the likely spread of results from repeated samples of size \mbox{$30$} and repeated samples of size \mbox{$1000$}.
\end{tasks}

\end{document}
