\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Perimeter and area of composite shapes involving circles — Excellence}}
\begin{tasks}(3)
\task A stadium shape has perimeter \mbox{$56 + 16\pi$} cm. Each semicircular end has radius 8 cm. Find the length of one straight side.
\task A stadium shape has straight sides of 24 m and semicircular ends of radius 6 m. Find the area enclosed. Give the exact answer in terms of \mbox{$\pi$}.
\task A rectangle 20 cm by 12 cm has a semicircle of diameter 12 cm attached externally to one short side. Find the perimeter and the area in terms of \mbox{$\pi$}.
\task A rectangle 18 cm by 10 cm has a semicircle of diameter 10 cm cut out from one short side. Find the perimeter and the remaining area in terms of \mbox{$\pi$}.
\task A square of side 16 cm has a quarter circle of radius 16 cm removed from one corner. Find the perimeter of the remaining shape in terms of \mbox{$\pi$}.
\task A square of side 16 cm has a quarter circle of radius 16 cm removed from one corner. Find the remaining area in terms of \mbox{$\pi$}.
\task Two semicircles of diameter 10 cm are attached to opposite short sides of a rectangle 18 cm by 10 cm. Find the perimeter in terms of \mbox{$\pi$}.
\task Two semicircles of diameter 10 cm are attached to opposite short sides of a rectangle 18 cm by 10 cm. Find the area in terms of \mbox{$\pi$}.
\task A square has side 14 m. Four quarter circles of radius 7 m are drawn inside it to make one full circle. Find the fraction of the square that is not part of the circle.
\task A shape is made from a semicircle of radius 9 cm on top of a rectangle 18 cm by 9 cm. If fencing costs 12 dollars per cm around the outside edge, find the total fencing cost in terms of \mbox{$\pi$}.
\task A running track has area \mbox{$1800 + 225\pi$} m\mbox{$^2$}. The two semicircular ends each have radius 15 m. Find the length of one straight section.
\task A rectangle is 30 cm by 14 cm. A semicircle of diameter 14 cm is attached to one short side and an identical semicircle is cut from the opposite short side. Find the total area of the final shape.
\task A rectangle is 30 cm by 14 cm. A semicircle of diameter 14 cm is attached to one short side and an identical semicircle is cut from the opposite short side. Find the perimeter of the final shape in terms of \mbox{$\pi$}.
\task A square of side 20 cm has a quarter circle of radius 10 cm removed from each corner. Find the remaining area in terms of \mbox{$\pi$}.
\task A square of side 20 cm has a quarter circle of radius 10 cm removed from each corner. Find the perimeter of the remaining central shape in terms of \mbox{$\pi$}.
\task A capsule-shaped logo has area \mbox{$300 + 36\pi$} cm\mbox{$^2$}. The two semicircular ends each have radius 6 cm. Find the length of the rectangle part.
\end{tasks}

\end{document}
