\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Excellence}}
\begin{tasks}(3)
\task Using a linear model, predict the test score for a student who studies 8 hours. Discuss your confidence in this prediction considering variation at that point.
\task Compare predictions from two different lines of best fit derived from different samples of the same population. Explain why they might differ.
\task Explain why extrapolation beyond the range of data may be unreliable for a linear model.
\task Discuss the effect of outliers on the line of best fit and the correlation coefficient.
\task Given a residual plot that shows a curved pattern, comment on the appropriateness of a linear model.
\task Explain the difference between correlation and causation in the context of a study linking ice cream sales and drowning incidents.
\task Discuss sampling variation: if another sample of the same size is taken, how might the line of best fit differ?
\task Use the linear model to make a prediction and suggest a reasonable range (confidence interval) for that prediction.
\task Evaluate the limitations of a linear model for predicting house prices based on number of rooms.
\task Given a scenario where data collection was biased, suggest improvements to obtain a more reliable linear model.
\task Interpret a coefficient of determination \(r^2 = 0.64\) in the context of a study on exercise and heart health.
\task Discuss the impact of a non-linear relationship (e.g., exponential) on the suitability of a linear model.
\end{tasks}

\end{document}