\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Foundation}}
\begin{tasks}(3)
\task A scatter plot shows the relationship between hours studied and test score. A line of best fit is drawn. Use the line to predict the test score for 5 hours of study.
\task A scatter plot shows height vs shoe size. A line of best fit is drawn. Predict shoe size for a height of 160 cm.
\task A scatter plot shows temperature vs ice cream sales. A line of best fit is drawn. Predict ice cream sales when the temperature is 30\textdegree C.
\task A scatter plot shows age vs reaction time. A line of best fit is drawn. Predict reaction time for a 20-year-old.
\task A scatter plot shows distance from city centre vs rent. A line of best fit is drawn. Predict rent for a house 10 km from the city centre.
\task A scatter plot shows number of pages vs weight of a book. A line of best fit is drawn. Predict the weight of a book with 200 pages.
\task A scatter plot shows engine size vs fuel consumption. A line of best fit is drawn. Predict fuel consumption for a 2.0 L engine.
\task A scatter plot shows years of experience vs salary. A line of best fit is drawn. Predict salary for someone with 10 years of experience.
\task A scatter plot shows rainfall vs crop yield. A line of best fit is drawn. Predict crop yield for 500 mm of rainfall.
\task A scatter plot shows advertising spend vs sales. A line of best fit is drawn. Predict sales for \$1000 spent on advertising.
\task A scatter plot shows speed vs stopping distance. A line of best fit is drawn. Predict stopping distance at 50 km/h.
\task A scatter plot shows number of rooms vs house price. A line of best fit is drawn. Predict house price for a house with 4 rooms.
\end{tasks}

\end{document}