\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Proficient}}
\begin{tasks}(3)
\task Given the line of best fit \(y = 2.5x + 10\), predict \(y\) when \(x = 6\).
\task Interpret the slope of the line \(y = 0.8x + 5\) in the context of hours studied vs test score.
\task Given the line of best fit \(y = -1.2x + 50\), predict \(x\) when \(y = 20\).
\task A scatter plot shows a strong positive correlation. Which of the following correlation coefficients is most likely: \(0.9\), \(0.2\), \(-0.7\)?
\task Calculate the residual for the data point \((3, 15)\) if the line of best fit predicts \(y = 14\).
\task The line of best fit passes through the points \((2, 5)\) and \((6, 13)\). Find its equation.
\task Using the equation from question 6, predict \(y\) when \(x = 10\).
\task For the line of best fit \(y = 3x + 4\), interpret the \(y\)-intercept in context.
\task Given a scatter plot with outliers, explain how removing an outlier would affect the line of best fit.
\task A line of best fit has equation \(y = 0.5x + 20\). Predict \(y\) for \(x = 30\) and comment on whether this extrapolation is reliable.
\task Compare two lines of best fit: one with slope \(2.0\) and one with slope \(0.5\). Which indicates a stronger relationship?
\task Given a residual plot that shows a random scatter, what does this suggest about the linear model?
\end{tasks}

\end{document}