\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Planning and collecting multivariate data — Excellence}}
\begin{tasks}(3)
\task Design a study to investigate the relationship between two variables (e.g., study time and test scores). Include a statistical question, population, and sampling method.
\task For your study, identify at least one categorical and one numerical variable.
\task Explain how you would ensure your sample is representative of the population.
\task Describe a stratified sampling plan that accounts for a relevant categorical variable.
\task What is sampling variation and how does sample size affect it?
\task Explain the concept of 'bias' in the context of your study.
\task How could non‑response bias affect your results?
\task What is the difference between random sampling and random allocation?
\task Discuss ethical considerations when collecting data from people.
\task How would you pilot your data‑collection instrument?
\task What is the purpose of a control group in an experiment?
\task Explain the difference between observational study and experiment.
\task How might confounding variables affect your study?
\task Describe how you would use a random number generator to select a simple random sample.
\task What is the 'margin of error' and how is it related to sample size?
\task Why is it important to clearly define variables before collecting data?
\end{tasks}

\end{document}
