\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Spatial patterns (including drawing next pattern and converting to pattern) --- Excellence}}
\begin{tasks}(3)
\task An L-shape pattern has counts \mbox{$5,\ 7,\ 9$}. Draw Pattern 5 and explain how you know the number of tiles without counting one by one.
\task A staircase pattern has counts \mbox{$3,\ 6,\ 10$}. Draw Pattern 4 and Pattern 5. How many extra tiles are added each time?
\task A row pattern has counts \mbox{$5,\ 8,\ 11,\ 14$}. Which pattern number has 35 tiles? Explain.
\task An L-shape pattern has counts \mbox{$7,\ 9,\ 11,\ 13$}. Which pattern number has 31 tiles? Explain.
\task A staircase pattern has counts \mbox{$3,\ 6,\ 10,\ 15$}. Is it increasing by a constant amount? Explain using the differences.
\task Two students convert the same picture pattern into numbers. Ari gets \mbox{$4,\ 7,\ 10,\ 13$}. Moana gets \mbox{$4,\ 8,\ 12,\ 16$}. Give one possible reason one of them is wrong.
\task Pattern 6 of a row pattern has 15 tiles. If the pattern grows by 2 tiles each time, what are the counts for Patterns 1 to 6?
\task Pattern 5 of an L-shape has 13 tiles. Work backwards to find the counts for Patterns 1 to 5.
\task A spatial pattern grows by 4 tiles each time. Pattern 3 has 18 tiles. Find the counts for Patterns 1 to 5.
\task Maia says: If a pattern uses more tiles each time, it must be adding the same number every term. Use one example to explain why this is not always true.
\task Create your own spatial pattern with square tiles where Pattern 1 has 4 tiles and Pattern 4 has 19 tiles. Draw or describe Patterns 1 to 4.
\task A pattern has counts \mbox{$6,\ 10,\ 14,\ 18$}. Another has \mbox{$4,\ 7,\ 10,\ 13$}. Compare the growth rules and say which reaches 30 tiles first.
\end{tasks}

\end{document}
