\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Spatial patterns (including drawing next pattern and converting to pattern) --- Foundation}}
\begin{tasks}(3)
\task Pattern 1 is a row of 2 tiles. Pattern 2 is a row of 3 tiles. Pattern 3 is a row of 4 tiles. Draw Pattern 4 and say how many tiles it has.
\task Pattern 1 is an L-shape with 3 tiles. Pattern 2 is an L-shape with 5 tiles. Pattern 3 is an L-shape with 7 tiles. Draw Pattern 4 and say how many tiles it has.
\task Pattern 1 is a staircase with 3 tiles. Pattern 2 is a staircase with 6 tiles. Pattern 3 is a staircase with 10 tiles. Draw Pattern 4 and say how many tiles it has.
\task Complete the row pattern table: term 1 \mbox{$=$} 2, term 2 \mbox{$=$} 3, term 3 \mbox{$=$} 4, term 4 \mbox{$=$} ? tiles.
\task Complete the L-shape pattern table: term 1 \mbox{$=$} 3, term 2 \mbox{$=$} 5, term 3 \mbox{$=$} 7, term 4 \mbox{$=$} ? tiles.
\task Complete the staircase pattern table: term 1 \mbox{$=$} 3, term 2 \mbox{$=$} 6, term 3 \mbox{$=$} 10, term 4 \mbox{$=$} ? tiles.
\task A growing pattern has tile counts \mbox{$3,\ 5,\ 7,\ 9$}. Draw a simple square-tile picture for term 1, 2, and 3.
\task A pattern has tile counts \mbox{$2,\ 3,\ 4,\ 5$}. Describe what happens from one term to the next.
\task A pattern has tile counts \mbox{$4,\ 7,\ 10,\ 13$}. How many tiles should Pattern 5 have?
\task A row pattern starts with 2 tiles in term 1 and adds 1 tile each time. Which term has 6 tiles?
\task An L-shape pattern starts with 3 tiles in term 1 and adds 2 tiles each time. Which term has 11 tiles?
\task Sofia says the staircase pattern \mbox{$3,\ 6,\ 10$} adds 2 tiles each time. Is she correct? Explain.
\end{tasks}

\end{document}
