\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Spatial patterns (including drawing next pattern and converting to pattern) --- Proficient}}
\begin{tasks}(3)
\task Pattern 1 is a row of 3 tiles. Pattern 2 is a row of 5 tiles. Pattern 3 is a row of 7 tiles. Draw Pattern 4 and write the tile counts for terms 1 to 4.
\task Pattern 1 is an L-shape with 5 tiles. Pattern 2 has 7 tiles. Pattern 3 has 9 tiles. Draw Pattern 4 and write the tile counts for terms 1 to 4.
\task Pattern 1 is a T-shape with 4 tiles. Pattern 2 has 7 tiles. Pattern 3 has 10 tiles. Draw Pattern 4 and write the tile counts for terms 1 to 4.
\task For the row pattern with counts \mbox{$3,\ 5,\ 7,\ 9$}, which pattern number has 15 tiles?
\task For the L-shape pattern with counts \mbox{$5,\ 7,\ 9,\ 11$}, which pattern number has 17 tiles?
\task For the T-shape pattern with counts \mbox{$4,\ 7,\ 10,\ 13$}, how many tiles are in Pattern 8?
\task A picture pattern gives the number pattern \mbox{$6,\ 8,\ 10,\ 12$}. Describe one possible square-tile design for it.
\task Another picture pattern gives \mbox{$5,\ 8,\ 11,\ 14$}. How many tiles would Pattern 10 have?
\task Hana says Pattern 5 has 12 tiles. The first four counts are \mbox{$3,\ 5,\ 7,\ 9$}. Is Hana correct? Explain.
\task A spatial pattern starts with 6 tiles and adds 3 tiles each time. Draw Patterns 1, 2, and 3, then state Pattern 6.
\task Which grows faster: \mbox{$2,\ 5,\ 8,\ 11$} or \mbox{$4,\ 8,\ 12,\ 16$}? Explain using the change each time.
\task A pattern is made from square tiles. Pattern 1 has 4 tiles and Pattern 5 has 20 tiles. If it grows by the same amount each time, write the counts for Patterns 1 to 5.
\end{tasks}

\end{document}
