\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Excellence}}
\begin{tasks}(3)
\task A student says \mbox{$\sqrt{9}$} is irrational because it has a square root sign. Are they correct? Explain.
\task A student says \mbox{$3.14159$} is irrational because it has many decimal places. Are they correct? Explain.
\task A student says \mbox{$0.272727\ldots$} is irrational because it never ends. Are they correct? Explain.
\task Which is greater: \mbox{$\sqrt{11}$} or \mbox{$3.3$}? Show enough working to justify.
\task Which is smaller: \mbox{$\sqrt{15}$} or \mbox{$3.9$}? Explain how you know.
\task Put in ascending order: \mbox{$\sqrt{2}, 1.41, 1.5, \frac{3}{2}$}.
\task Put in ascending order: \mbox{$3, \pi, \sqrt{10}, 3.2$}.
\task Which does not belong: \mbox{$\sqrt{2}, \pi, \frac{7}{3}, \sqrt{7}$}?
\task Find one rational number between \mbox{$\sqrt{2}$} and \mbox{$\sqrt{3}$}.
\task Find one irrational number between \mbox{$2$} and \mbox{$3$}.
\task Is \mbox{$\sqrt{18}=3\sqrt{2}$} rational or irrational? Explain.
\task Is \mbox{$2\pi$} rational or irrational? Explain.
\task Complete: if \mbox{$n$} is a whole number and \mbox{$\sqrt{n}$} is rational, then one possible value of \mbox{$n$} is \rule{1.6cm}{0.15mm}.
\task Complete: an irrational number between \mbox{$4$} and \mbox{$5$} is \rule{1.8cm}{0.15mm}.
\task True or false: the decimal for an irrational number can terminate. Explain.
\task True or false: \mbox{$\frac{22}{7}$} is irrational because it is close to \mbox{$\pi$}. Explain.
\task A number lies between \mbox{$\sqrt{5}$} and \mbox{$\sqrt{6}$}. Is it definitely irrational? Explain.
\task Explain why not every non-terminating decimal is irrational.
\end{tasks}

\end{document}
