\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Representing and constructing 3D shapes --- Excellence}}
\begin{tasks}(3)
\task A solid has \mbox{$5$} faces, \mbox{$9$} edges, and \mbox{$6$} vertices. Explain why it cannot be a square-based pyramid.
\task A solid has \mbox{$6$} faces, \mbox{$12$} edges, and \mbox{$8$} vertices. Give two different ways to recognise it from those facts.
\task Draw two different valid nets for the same rectangular prism. Explain why both fold to the same solid.
\task A student says, ``Any arrangement of \mbox{$6$} rectangles can be a rectangular prism net.'' Give a counterexample and explain it.
\task A triangular prism has equilateral triangular ends of side \mbox{$5\text{ cm}$} and prism length \mbox{$9\text{ cm}$}. Draw a correct net and label all face dimensions.
\task State which faces in your triangular prism net are congruent.
\task A square-based pyramid has base side \mbox{$8\text{ cm}$}. Draw a net and describe what must be true about the \mbox{$4$} triangular faces.
\task Explain why the plan view of a standing square-based pyramid is a square but the front view is a triangle.
\task A rectangular prism measures \mbox{$10\text{ cm}$} by \mbox{$6\text{ cm}$} by \mbox{$4\text{ cm}$}. Describe its plan view, front view, and side view.
\task A student draws a net for a triangular prism but attaches both triangles to the same long rectangle in a way that causes overlap when folded. What needs to change?
\task Why can a correct net show all faces of a solid at once, but a plan view cannot?
\task Design a net for a solid with \mbox{$5$} faces and \mbox{$8$} edges. Name the solid and explain how you know your net is correct.
\task Compare a rectangular prism and a triangular prism. Give one similarity and two differences in faces, edges, or vertices.
\task Compare a triangular prism and a square-based pyramid. Give one similarity and two differences in faces, edges, or vertices.
\task Explain why opposite faces of a rectangular prism are congruent.
\task A solid has a rectangular plan view and a rectangular front view. Could it be a square-based pyramid? Explain your answer.
\end{tasks}

\end{document}
