\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Representing and constructing 3D shapes --- Foundation}}
\begin{tasks}(3)
\task Name the solid with \mbox{$6$} rectangular faces.
\task Name the solid with \mbox{$2$} triangular faces and \mbox{$3$} rectangular faces.
\task Name the solid with \mbox{$1$} square base and \mbox{$4$} triangular faces.
\task How many faces does a rectangular prism have?
\task How many edges does a triangular prism have?
\task How many vertices does a square-based pyramid have?
\task Which solid has exactly \mbox{$5$} faces: a rectangular prism, a triangular prism, or a square-based pyramid?
\task Which solid has exactly \mbox{$8$} vertices: a rectangular prism, a triangular prism, or a square-based pyramid?
\task Draw one valid net for a rectangular prism.
\task Draw one valid net for a triangular prism.
\task Draw one valid net for a square-based pyramid.
\task A rectangular prism has length \mbox{$6\text{ cm}$}, width \mbox{$4\text{ cm}$}, and height \mbox{$3\text{ cm}$}. Draw and label one net.
\task A triangular prism has triangular ends and \mbox{$3$} rectangular side faces. Which faces in the net must be congruent?
\task Explain what a net shows about a 3D shape.
\end{tasks}

\end{document}
