\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Excellence: Solving inequalities}}
\begin{tasks}(3)
\task Solve: \mbox{$5 - 3x > 14$}
\task Solve: \mbox{$8 - 2y \le 2$}
\task Solve: \mbox{$3(2a - 4) \ge 24$}
\task Solve: \mbox{$\frac{2b + 6}{3} < 10$}
\task Solve: \mbox{$4(c - 3) + 2c > 30$}
\task Solve: \mbox{$\frac{5d - 10}{2} \le 15$}
\task Solve: \mbox{$2(e + 4) - 3e < 5$}
\task Solve: \mbox{$\frac{3f + 9}{4} \ge 6$}
\task Solve: \mbox{$5 - 2(g + 1) > 1$}
\task Solve: \mbox{$\frac{4h - 8}{2} \le 10$}
\task Solve: \mbox{$3(2k - 5) + k \ge 20$}
\task Solve: \mbox{$\frac{5m + 15}{3} < 25$}
\task Solve: A taxi ride costs a \mbox{$5 fee plus \$}2 per kilometre, \mbox{$k$}. If you have a maximum budget of \$25, write an inequation and solve it to find the maximum distance you can travel.
\task Solve: You need at least 80 marks to pass a test. Each correct answer is worth 4 marks. If you answered \mbox{$x$} questions correctly, write an inequation and solve it to find the minimum number of correct answers needed.
\task Solve: A rectangle has length \mbox{$2x + 3$} and width \mbox{$x$}. If the perimeter is at most 36 cm, write an inequation and solve it to find the possible values of \mbox{$x$}.
\task Solve: The sum of three consecutive integers is less than 60. If the smallest integer is \mbox{$n$}, write an inequation and solve it to find the possible values of \mbox{$n$}.
\task Solve: A phone plan costs \mbox{$20 per month plus \$}0.10 per minute of calls. If you want to spend at most \$50 per month, write an inequation and solve it to find the maximum minutes you can use.
\task Solve: You are saving for a \mbox{$120 bike. You already have \$}45 and can save \$15 per week. Write an inequation and solve it to find how many weeks you need to save.
\task Solve: A number is multiplied by 4, then 7 is subtracted. The result is greater than 25. Write an inequation and solve it to find the possible numbers.
\task Solve: Half of a number plus 8 is at most 20. Write an inequation and solve it to find the possible numbers.
\end{tasks}

\end{document}