\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Forming measurement expressions --- Excellence}}
\begin{tasks}(3)
\task A rectangle has length \mbox{$x+2$} and width \mbox{$x-1$}. Write a simplified perimeter.
\task A rectangle has length \mbox{$3y$} and width \mbox{$y+4$}. Write a simplified perimeter.
\task A square has side \mbox{$2a+1$}. Write a simplified perimeter.
\task An equilateral triangle has side \mbox{$t+5$}. Write a simplified perimeter.
\task A cuboid has length \mbox{$x$}, width \mbox{$x+1$}, height \mbox{$4$}. Write its volume.
\task A tank starts with \mbox{$25$} L and fills at \mbox{$3n$} L/min for \mbox{$m$} minutes. Write the amount after \mbox{$m$} minutes.
\task A return trip is twice the one-way distance \mbox{$d+7$}. Write a simplified total distance.
\task Two rows use \mbox{$k$} and \mbox{$k+3$} tiles. Each tile is \mbox{$0.5$} m long. Write the total row length.
\task A student writes a rectangle perimeter as \mbox{$2l+w$}. What is missing? Write the correct expression.
\task A square and an equilateral triangle both have side \mbox{$p$}. Write the difference between their perimeters.
\task A cube has edge \mbox{$n+2$}. Write the total length of all \mbox{$12$} edges.
\task A roll is cut into \mbox{$x$} pieces of \mbox{$2.5$} m and \mbox{$3$} extra pieces of \mbox{$1$} m. Write the total length used.
\task A runner travels at \mbox{$8$} km/h for \mbox{$h$} hours, then \mbox{$2$} more hours. Write a simplified distance.
\task A rectangle has width \mbox{$w$} and length \mbox{$w+6$}. Write one perimeter expression and one equivalent simplified form.
\task The area of a rectangle is \mbox{$x(x+4)$}. What could the side lengths be?
\task A prism has cross-sectional area \mbox{$A$} and length \mbox{$l$}. Write its volume and say what each variable means.
\end{tasks}

\end{document}
