\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Pythagoras theory finding short and long sides --- Excellence}}
\begin{tasks}(3)
\task A right-angled triangle has short sides 9 cm and 40 cm. Find the long side.
\task A right-angled triangle has a long side of 41 cm and one short side of 9 cm. Find the other short side.
\task The short sides are 12 m and 16 m. Find the long side.
\task The long side is 29 m and one short side is 20 m. Find the other short side.
\task The short sides are 7 cm and 24 cm. Find the long side.
\task The long side is 25 cm and one short side is 24 cm. Find the other short side.
\task A right-angled triangle has short sides 2.4 m and 3.2 m. Find the long side.
\task A right-angled triangle has a long side of 10 cm and one short side of 6 cm. Find the other short side.
\task A right-angled triangle has short sides 9 cm and 13 cm. Find the long side to 2 decimal places.
\task A right-angled triangle has a long side of 13 m and one short side of 5 m. Find the other short side to 2 decimal places.
\task A right-angled triangle has perimeter 36 cm. Its short sides are 9 cm and 12 cm. Find the long side and check the perimeter.
\task A right-angled triangle has perimeter 56 cm. The long side is 20 cm and one short side is 16 cm. Find the third side and decide if the perimeter claim is true.
\task The long side of a right-angled triangle is 15 cm. Which could be the missing short side: 8 cm, 9 cm, or 12 cm if the other short side is 9 cm? Explain briefly.
\task A student says \mbox{$8^2 + 15^2 = 17^2$}, so a triangle with sides 8 cm, 15 cm, and 17 cm is right-angled. Is the student correct?
\task A right-angled triangle has one short side 18 cm and the other short side is 6 cm shorter. Find the long side.
\task A right-angled triangle has a long side of 34 cm and one short side of 30 cm. Find the other short side.
\end{tasks}

\end{document}
