\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Pythagoras theory finding short and long sides --- Foundation}}
\begin{tasks}(3)
\task A right-angled triangle has short sides 3 cm and 4 cm. Find the long side.
\task A right-angled triangle has short sides 5 m and 12 m. Find the long side.
\task A right-angled triangle has short sides 6 cm and 8 cm. Find the long side.
\task A right-angled triangle has a long side of 5 cm and one short side of 3 cm. Find the other short side.
\task A right-angled triangle has a long side of 13 m and one short side of 12 m. Find the other short side.
\task A right-angled triangle has a long side of 17 mm and one short side of 8 mm. Find the other short side.
\task A right-angled triangle has short sides 4 cm and 7 cm. Find the long side to 1 decimal place.
\task A right-angled triangle has short sides 4 m and 9 m. Find the long side to 1 decimal place.
\task A right-angled triangle has a long side of 10 cm and one short side of 8 cm. Find the other short side.
\task A right-angled triangle has a long side of 13 cm and one short side of 12 cm. Find the other short side.
\task A right-angled triangle has short sides 9 cm and 12 cm. Find the long side.
\task A right-angled triangle has a long side of 15 m and one short side of 9 m. Find the other short side.
\task A right-angled triangle has short sides 1.2 m and 1.6 m. Find the long side.
\task True or false: in a right-angled triangle, the long side is always opposite the right angle.
\end{tasks}

\end{document}
