\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Pythagoras theory finding short and long sides --- Proficient}}
\begin{tasks}(3)
\task A right-angled triangle has short sides 9 cm and 12 cm. Find the long side.
\task A right-angled triangle has a long side of 25 cm and one short side of 24 cm. Find the other short side.
\task A right-angled triangle has short sides 7 m and 11 m. Find the long side to 1 decimal place.
\task A right-angled triangle has a long side of 11.7 cm and one short side of 6 cm. Find the other short side to 1 decimal place.
\task One short side is 14 cm and the long side is 20 cm. Find the other short side.
\task The two short sides are 6.5 m and 7.2 m. Find the long side to 1 decimal place.
\task One short side is 10 mm and the long side is 26 mm. Find the other short side.
\task The two short sides are 15 cm and 8 cm. Find the long side.
\task A right-angled triangle has area \mbox{$24\text{ cm}^2$} and one short side is 6 cm. Find the other short side, then find the long side.
\task A right-angled triangle has a long side of 17 cm and one short side of 15 cm. Find the other short side and check whether it is a whole number.
\task The long side of a right-angled triangle is 13 m. One short side is 5 m. Find the other short side.
\task The short sides of a right-angled triangle differ by 7 cm. If one short side is 24 cm, find the other short side and then the long side.
\end{tasks}

\end{document}
