\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Pythagorean triples — Proficient}}
\begin{tasks}(3)
\task Show whether \mbox{$(9,40,41)$} is a Pythagorean triple.
\task Show whether \mbox{$(12,35,37)$} is a Pythagorean triple.
\task Show whether \mbox{$(10,24,25)$} is a Pythagorean triple.
\task A right-angled triangle has short sides 12 cm and 16 cm. Write the triple in simplest whole-number form.
\task A right-angled triangle has short sides 15 m and 20 m. Write the triple in simplest whole-number form.
\task The hypotenuse is 25 cm and one short side is 7 cm. Find the missing side and write the triple.
\task The hypotenuse is 17 m and one short side is 8 m. Find the missing side and write the triple.
\task The hypotenuse is 37 mm and one short side is 35 mm. Find the missing side and write the triple.
\task If \mbox{$(5,12,13)$} is a Pythagorean triple, write the triple formed by multiplying by 3.
\task If \mbox{$(8,15,17)$} is a Pythagorean triple, write the triple formed by multiplying by 4.
\task One side length is 18 cm. Complete a Pythagorean triple by scaling \mbox{$(3,4,5)$}.
\task Explain briefly why multiplying every side in a Pythagorean triple by the same integer gives another Pythagorean triple.
\end{tasks}

\end{document}
