\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Excellence}}
\begin{tasks}(3)
\task An investment grows by 5\% per year for 2 years and is now \$11,025. What was the initial investment?
\task A population decreases by 8\% each year for 3 years and is now 778,688. What was the original population?
\task A price is increased by 20\% then decreased by 20\%. The final price is \$96. What was the original price?
\task A number is increased by 25\% and then decreased by 40\% to become 75. What was the original number?
\task After a 10\% discount and then a surcharge of 5 dollars, the price is 86 dollars. What was the original price?
\task A salary increased by 15\% and then by a further 10\% to become \$5060. What was the original salary?
\task A rectangle's length increased by 20\% and width decreased by 10\%, and the area became 432 square centimetres. What was the original area?
\task A car's price increased by 20\% and then decreased by 2000 dollars to become 28,000 dollars. What was the original price?
\task A shop offers 30\% off, then an additional 10\% off the discounted price. The final price is \$126. What was the original price?
\task A stock price fell by 10\% then rose by 10\% to become \$99. What was the original price?
\task After a 12.5\% tax, a meal costs \$45. What was the pre-tax cost?
\task A jacket is on sale for \$144 after a 20\% discount. What was the original price?
\end{tasks}

\end{document}
