\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Volume of other 3D shapes (cylinders, cones, pyramids, spheres, etc) --- Excellence}}
\begin{tasks}(3)
\task A cylinder and a sphere both have radius 6 cm. The cylinder has height 8 cm. Which has the greater volume, and by how much? Give your answer in terms of \mbox{$\pi$}.
\task A cone and a cylinder have the same radius and the same height. Explain why the cylinder's volume is three times the cone's volume.
\task A square pyramid has base side 12 cm. Its volume is 576 cm\mbox{$^3$}. Find the perpendicular height.
\task A sphere has the same volume as a cylinder with radius 3 cm and height 16 cm. Form an equation and solve for the sphere's radius exactly.
\task A cone has volume \mbox{$128\pi$} cm\mbox{$^3$} and height 24 cm. Find the radius.
\task A cylindrical tank has diameter 10 m and depth 4 m. It is \mbox{$70\%$} full. How many cubic metres of water are in the tank? Give your answer correct to 1 decimal place.
\task A square pyramid has the same base area and height as a prism. The prism volume is 540 cm\mbox{$^3$}. Find the pyramid volume and justify your answer.
\task A sphere has radius \mbox{$r$}. Write an expression for the volume of a hemisphere in terms of \mbox{$r$}.
\task A cone has radius 9 cm and slant height 15 cm. Find its perpendicular height, then its volume in terms of \mbox{$\pi$}.
\task A cylinder has radius 4 cm. Its volume is the same as a cone with radius 8 cm. Find the ratio of the cylinder height to the cone height.
\task A solid metal sphere of radius 6 cm is melted and recast into a cylinder of radius 3 cm. Find the height of the cylinder.
\task A square pyramid has volume 250 cm\mbox{$^3$} and height 6 cm. Find the side length of the base correct to 1 decimal place.
\task A toy is made from a hemisphere of radius 4 cm joined to a cone of radius 4 cm and height 9 cm. Find the total volume in terms of \mbox{$\pi$}.
\task A sphere has volume \mbox{$288\pi$} cm\mbox{$^3$}. Form an equation and solve for the radius.
\task A cone and a pyramid both have volume 180 cm\mbox{$^3$}. The cone has radius 6 cm. The pyramid has square base side 6 cm. Find the height of each solid.
\task A cylinder has radius 5 cm and volume \mbox{$200\pi$} cm\mbox{$^3$}. If the radius is doubled and the height is halved, what is the new volume?
\end{tasks}

\end{document}
