\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Applying Pythagoras’ Theory to 3D representations --- Excellence}}
\begin{tasks}(3)
\task A cuboid is 6 cm by 8 cm by 24 cm. Find the space diagonal exactly.
\task A cuboid is 9 cm by 12 cm by 12 cm. Find the space diagonal exactly.
\task A cuboid is 5 cm by 12 cm by 20 cm. Find the space diagonal to 1 decimal place.
\task A room is 2.5 m wide, 6 m long, and 2.4 m high. Find the longest straight-line distance corner to corner.
\task A cuboid has a square base of side 10 cm. Its space diagonal is 18 cm. Find the height to 1 decimal place.
\task The space diagonal of a cuboid is 41 cm. Two edges are 9 cm and 12 cm. Find the third edge.
\task A box is 15 cm long and 8 cm deep. Its longest inside diagonal is 20 cm. Find the height to 1 decimal place.
\task A package measures 20 cm by 21 cm by 48 cm. Will a 56 cm stick fit inside it? Justify your answer.
\task A cuboid has dimensions \mbox{$x$} cm, \mbox{$x$} cm, and 24 cm. Its space diagonal is 26 cm. Find \mbox{$x$}.
\task A display case is 30 cm by 40 cm by 90 cm. Find the shortest whole-number rod that will reach from one corner to the opposite corner.
\task A cuboid has base diagonal 25 cm and height 24 cm. Find the space diagonal. State whether it is a whole number.
\task A storage crate is 1.8 m by 2.4 m by 6 m. Find the longest inside diagonal exactly in surd form, then to 1 decimal place.
\task A cuboid has side lengths in the ratio \mbox{$3:4:12$}. The shortest side is 5 cm. Find the space diagonal to 1 decimal place.
\task A rectangular prism has width 9 cm. The face diagonal across width and height is 15 cm, and the full space diagonal is 36 cm. Find the length.
\task A cuboid has integer side lengths and space diagonal 17 cm. One edge is 8 cm and another is 15 cm. Find the third edge and say what is special.
\task A builder wants a brace across a box frame measuring 12 dm by 16 dm by 21 dm. Find the brace length to 1 decimal place.
\end{tasks}

\end{document}
