\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Applying Pythagoras’ Theory to 3D representations --- Foundation}}
\begin{tasks}(3)
\task A cuboid is 6 cm long, 4 cm wide, and 3 cm high. Find the diagonal across the base.
\task A cuboid is 8 m long, 6 m wide, and 2 m high. Find the diagonal across the base to 1 decimal place.
\task A cuboid is 9 cm long, 12 cm wide, and 5 cm high. Find the diagonal across the base.
\task A box is 5 cm long, 12 cm high, and 4 cm deep. Find the diagonal across the front face.
\task A room is 3 m wide, 4 m high, and 5 m long. Find the diagonal across the 3 m by 4 m wall.
\task A prism is 7 cm long, 24 cm high, and 10 cm deep. Find the diagonal across the front face.
\task A cuboid is 6 cm long, 8 cm wide, and 2 cm high. Find the space diagonal to 1 decimal place.
\task A cuboid is 9 m long, 12 m wide, and 4 m high. Find the space diagonal to 1 decimal place.
\task A cuboid is 3 cm long, 4 cm wide, and 12 cm high. Find the space diagonal.
\task A fish tank is 8 cm by 15 cm by 4 cm. Find the longest inside diagonal to 1 decimal place.
\task A storage box is 5 cm by 12 cm by 13 cm. Find the longest inside diagonal to 1 decimal place.
\task A cabinet is 1.2 m by 1.6 m by 2.0 m. Find the longest inside diagonal to 1 decimal place.
\task A cuboid has base edges 5 cm and 12 cm, and height 9 cm. Find the base diagonal first, then the space diagonal.
\task A gift box is 9 cm by 12 cm by 20 cm. Which is longer: a face diagonal or the full space diagonal?
\end{tasks}

\end{document}
