\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Applying Pythagoras’ Theory to 3D representations --- Proficient}}
\begin{tasks}(3)
\task A cuboid is 8 cm by 6 cm by 24 cm. Find the space diagonal to 1 decimal place.
\task A cuboid is 10 m by 24 m by 7 m. Find the space diagonal to 1 decimal place.
\task A cuboid is 9 cm by 12 cm by 20 cm. Find the space diagonal exactly if possible.
\task A room is 4 m wide, 3 m high, and 12 m long. Find the distance from one floor corner to the opposite ceiling corner.
\task A crate is 5 cm by 12 cm by 84 cm. Find its longest inside diagonal.
\task A cuboid has base diagonal 15 cm and height 8 cm. Find the space diagonal.
\task The space diagonal of a cuboid is 13 cm. Its height is 12 cm and its depth is 4 cm. Find the length.
\task The space diagonal of a box is 17 cm. Its length is 8 cm and its depth is 15 cm. Find the height.
\task A cuboid is 6 cm high and has a square base. The space diagonal is 11 cm. Find the side length of the base to 1 decimal place.
\task A tunnel frame is 9 m wide and 12 m high. A support runs across that rectangular face. Find the support length.
\task A shipping box is 30 cm by 40 cm by 120 cm. Can a 130 cm rod fit exactly along the inside diagonal? Explain.
\task A cuboid has dimensions 2.4 m, 3.2 m, and 6 m. Find the longest inside diagonal to 1 decimal place.
\end{tasks}

\end{document}
