\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Drawing nets of basic shapes --- Excellence}}
\begin{tasks}(3)
\task Draw two different valid nets for a cube. Explain how you know they are different.
\task A student says, ``Any 6 joined squares make a cube net.'' Give a counterexample and explain it.
\task A cuboid has dimensions \mbox{$8\text{ cm}$} by \mbox{$5\text{ cm}$} by \mbox{$3\text{ cm}$}. Draw a correct net and label all face dimensions.
\task A student drew a cuboid net using only rectangles of size \mbox{$8\times 5$} and \mbox{$8\times 3$}. What face type is missing, and why does that matter?
\task Draw a net for a triangular prism with equilateral triangular ends of side \mbox{$4\text{ cm}$} and prism length \mbox{$9\text{ cm}$}.
\task Name all pairs of congruent faces in your triangular prism net.
\task Draw a net for a square-based pyramid with base side \mbox{$6\text{ cm}$} and triangular faces of slant edge \mbox{$5\text{ cm}$}.
\task Explain why the 4 triangular faces of a square-based pyramid net are congruent when all side edges are equal.
\task A cube net is made from \mbox{$1\text{ cm}$} squares. What is the total area of the paper before folding?
\task A cuboid net has two faces of area \mbox{$24\text{ cm}^2$}, two faces of area \mbox{$18\text{ cm}^2$}, and two faces of area \mbox{$12\text{ cm}^2$}. Find one possible set of cuboid dimensions.
\task Explain why a net can show surface area directly but not volume directly.
\task Design a net for a solid that is not a cube. State the solid, label its faces, and explain how you know the net is correct.
\task A shape has 5 faces, 8 edges, and 5 vertices. Which basic solid could it be, and what might its net look like?
\task Compare a cube net and a square-based pyramid net. Give 2 similarities and 2 differences.
\task Why can two different nets fold to the same 3D shape? Use a cube or cuboid as your example.
\task Explain how congruent faces help you check whether a cuboid net is correct.
\end{tasks}

\end{document}
