\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Drawing nets of basic shapes --- Proficient}}
\begin{tasks}(3)
\task Draw two different valid nets for a cube.
\task Draw a net for a cuboid with length \mbox{$6\text{ cm}$}, width \mbox{$4\text{ cm}$}, and height \mbox{$2\text{ cm}$}.
\task Draw a net for a triangular prism whose triangular ends are right triangles with sides \mbox{$3\text{ cm}$}, \mbox{$4\text{ cm}$}, and \mbox{$5\text{ cm}$}.
\task Draw a net for a square-based pyramid with base side \mbox{$5\text{ cm}$}.
\task In a cube net, how many pairs of opposite faces will there be after folding?
\task In a triangular prism net, how many rectangular faces should appear?
\task In a square-based pyramid net, which face is the base?
\task A cuboid has face sizes \mbox{$8\times 3$}, \mbox{$8\times 2$}, and \mbox{$3\times 2$}. Sketch a net and state which faces are congruent.
\task Explain why a row of 6 equal squares does not make a cube net.
\task Explain one way to check whether a net will fold without faces overlapping.
\task A student draws a cube net with 5 squares only. Explain what is wrong.
\task A student draws a cuboid net but uses only 4 rectangles. Explain what is missing.
\end{tasks}

\end{document}
