\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Applying Pythagoras’ theory --- Excellence}}
\begin{tasks}(3)
\task A rectangle has perimeter 34 cm and width 7 cm. Find its diagonal.
\task A square has perimeter 48 cm. Find its diagonal.
\task An isosceles triangle has perimeter 50 cm and base 20 cm. Find its height.
\task An isosceles triangle has equal sides 29 cm and height 21 cm. Find the base.
\task A ladder stands 5 m from a wall and reaches 12 m up it. Find the ladder length.
\task A rectangle has diagonal 25 cm. One side is 7 cm shorter. Find both sides.
\task Sides 9 cm, 12 cm, 15 cm. Is the triangle right-angled? Explain.
\task Sides 11 cm, 60 cm, 61 cm. Is the triangle right-angled? Explain.
\task Sides 12 cm, 18 cm, 21 cm. Is the triangle right-angled? Explain.
\task A square has diagonal 18 cm. Find its area to 1 decimal place.
\task A photo is 20 cm by 21 cm. Find its diagonal to 1 decimal place.
\task An isosceles triangle has equal sides 13 cm and height 12 cm. Find the base.
\task Sides 16 cm, 30 cm, 34 cm. Is the triangle right-angled? Justify.
\task Sides 14 cm, 48 cm, 50 cm. Is the triangle right-angled? Justify.
\task A square has side 5.5 m. Find its diagonal to 2 decimal places.
\task A rectangle is 11 cm by 60 cm. Find its diagonal. Would a 61 cm brace fit exactly?
\end{tasks}

\end{document}
