\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Applying Pythagoras’ theory --- Foundation}}
\begin{tasks}(3)
\task A square has side length 6 cm. Find its diagonal.
\task A square has side length 9 m. Find its diagonal to 1 decimal place.
\task A rectangle is 5 cm by 12 cm. Find its diagonal.
\task A rectangle is 8 m by 15 m. Find its diagonal.
\task A television screen is 24 cm wide and 18 cm high. Find the screen diagonal.
\task A rectangle has diagonal 13 cm and width 5 cm. Find the height.
\task A rectangle has diagonal 17 m and length 15 m. Find the width.
\task An isosceles triangle has equal sides 13 cm and base 10 cm. Find its height.
\task An isosceles triangle has equal sides 10 cm and base 12 cm. Find its height.
\task A ladder reaches 12 m up a wall and is 13 m long. How far is the foot of the ladder from the wall?
\task A triangle has side lengths 3 cm, 4 cm, and 5 cm. Is it right-angled?
\task A triangle has side lengths 5 cm, 12 cm, and 13 cm. Is it right-angled?
\task A triangle has side lengths 6 cm, 8 cm, and 11 cm. Is it right-angled?
\task True or false: if the longest side of a triangle is 10 cm and the other sides are 6 cm and 8 cm, then the triangle is right-angled.
\end{tasks}

\end{document}
