\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Interpreting pie charts \& pictograms --- Excellence}}
\begin{tasks}(3)
\task This pie chart shows favourite subjects for 160 students.\\
\simplepie{{35/red/Maths,30/blue/Science,20/green/English,15/yellow/Other}}\\
How many more students chose Maths than Other?

\task This pie chart shows how \$2400 of camp money was spent.\\
\simplepie{{50/red/Travel,25/blue/Food,15/green/Gear,10/yellow/Other}}\\
How much was spent on Food and Gear altogether?

\task This pie chart shows sport choices for 90 students.\\
\simplepie{{40/red/Rugby,30/blue/Football,20/green/Netball,10/yellow/Other}}\\
How many students chose a sport other than rugby?

\task This pie chart shows favourite music styles.\\
\simplepie{{45/red/Pop,25/blue/Rock,20/green/Hip-hop,10/yellow/Other}}\\
Explain why Pop is not quite twice Hip-hop.

\task The pictogram shows books sold. Key: \picto{1}{B} = 8 books.\\[0.3em]
\begin{tabular}{ll}
Week 1 & \picto{5}{B} \\
Week 2 & \picto{3}{B} \\
Week 3 & \picto{6}{B}
\end{tabular}\\
How many books were sold in all three weeks?

\task The pictogram shows cups of soup sold. Key: \picto{1}{S} = 6 cups.\\[0.3em]
\begin{tabular}{ll}
Tomato   & \picto{4}{S} \\
Pumpkin  & \picto{3}{S} \\
Chicken  & \picto{5}{S}
\end{tabular}\\
How many more chicken soups were sold than pumpkin soups?

\task The pictogram shows points scored. Key: \picto{1}{P} = 5 points.\\[0.3em]
\begin{tabular}{ll}
Ava  & \picto{6}{P} \\
Noah & \picto{4}{P} \\
Tia  & \picto{5}{P}
\end{tabular}\\
Who scored the median number of points?

\task The pictogram shows bags packed for camp. Key: \picto{1}{C} = 3 bags.\\[0.3em]
\begin{tabular}{ll}
Cabin A & \picto{7}{C} \\
Cabin B & \picto{5}{C} \\
Cabin C & \picto{6}{C}
\end{tabular}\\
How many bags would Cabin A and Cabin C have together?

\task A pie chart shows that 15\% of 240 students chose drama. How many students chose drama?

\task A pie chart shows 35\% for one category and 25\% for another. What percentage is left for the other categories?

\task A pictogram uses 1 symbol to represent 7 items. If there are 56 items, how many symbols are needed?

\task A pictogram uses 1 symbol to represent 4 people. If 6 symbols are shown for Team A and 9 symbols for Team B, how many more people are in Team B?

\end{tasks}

\end{document}
