\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Interpreting pie charts \& pictograms --- Foundation}}
\begin{tasks}(3)
\task This pie chart shows favourite pets.\\
\simplepie{{40/red/Cats,30/blue/Dogs,20/green/Fish,10/yellow/Other}}\\
What percentage chose cats?

\task This pie chart shows how students travel to school.\\
\simplepie{{25/red/Walk,35/blue/Car,20/green/Bus,20/yellow/Bike}}\\
Which way is most popular?

\task This pie chart shows favourite fruits.\\
\simplepie{{30/red/Apple,30/blue/Banana,25/green/Orange,15/yellow/Grapes}}\\
What percentage chose grapes?

\task This pie chart shows sports choices.\\
\simplepie{{50/red/Rugby,20/blue/Netball,20/green/Football,10/yellow/Other}}\\
What percentage chose rugby and football altogether?

\task The pictogram shows books read last month. Key: \picto{1}{B} = 2 books.\\[0.3em]
\begin{tabular}{ll}
Aroha & \picto{3}{B} \\
Mika  & \picto{5}{B} \\
Luca  & \picto{2}{B}
\end{tabular}\\
How many books did Mika read?

\task The pictogram shows pets in three homes. Key: \picto{1}{P} = 1 pet.\\[0.3em]
\begin{tabular}{ll}
Home 1 & \picto{4}{P} \\
Home 2 & \picto{2}{P} \\
Home 3 & \picto{5}{P}
\end{tabular}\\
How many pets are in Home 3?

\task The pictogram shows goals scored. Key: \picto{1}{G} = 2 goals.\\[0.3em]
\begin{tabular}{ll}
Team A & \picto{4}{G} \\
Team B & \picto{3}{G} \\
Team C & \picto{2}{G}
\end{tabular}\\
How many goals did Team A score?

\task The pictogram shows apples picked. Key: \picto{1}{A} = 5 apples.\\[0.3em]
\begin{tabular}{ll}
Box 1 & \picto{2}{A} \\
Box 2 & \picto{4}{A} \\
Box 3 & \picto{3}{A}
\end{tabular}\\
How many apples are in Box 2?

\task Use this pie chart.\\
\simplepie{{45/red/Yes,55/blue/No}}\\
What percentage voted no?

\task Use this pictogram. Key: \picto{1}{C} = 3 cakes.\\[0.3em]
\begin{tabular}{ll}
Class 1 & \picto{2}{C} \\
Class 2 & \picto{5}{C} \\
Class 3 & \picto{4}{C}
\end{tabular}\\
How many cakes did Class 1 make?

\end{tasks}

\end{document}
