\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Interpreting pie charts \& pictograms --- Proficient}}
\begin{tasks}(3)
\task This pie chart shows favourite lunch choices for 80 students.\\
\simplepie{{35/red/Sandwich,25/blue/Sushi,20/green/Pasta,20/yellow/Other}}\\
How many students chose sushi?

\task This pie chart shows transport to school for 120 students.\\
\simplepie{{40/red/Car,25/blue/Walk,20/green/Bus,15/yellow/Bike}}\\
How many students travel by bike?

\task This pie chart shows club choices.\\
\simplepie{{30/red/Art,30/blue/Sport,25/green/Music,15/yellow/Drama}}\\
What percentage chose Art or Music?

\task This pie chart shows favourite games for 60 students.\\
\simplepie{{50/red/Football,20/blue/Basketball,20/green/Netball,10/yellow/Other}}\\
How many students did not choose football?

\task The pictogram shows books borrowed. Key: \picto{1}{B} = 4 books.\\[0.3em]
\begin{tabular}{ll}
Room 1 & \picto{3}{B} \\
Room 2 & \picto{5}{B} \\
Room 3 & \picto{4}{B}
\end{tabular}\\
How many books were borrowed altogether?

\task The pictogram shows goals scored. Key: \picto{1}{G} = 3 goals.\\[0.3em]
\begin{tabular}{ll}
Kea    & \picto{2}{G} \\
Tui    & \picto{4}{G} \\
Kakapo & \picto{3}{G}
\end{tabular}\\
How many more goals did Tui score than Kea?

\task The pictogram shows fruit boxes sold. Key: \picto{1}{F} = 6 boxes.\\[0.3em]
\begin{tabular}{ll}
Shop A & \picto{5}{F} \\
Shop B & \picto{2}{F} \\
Shop C & \picto{4}{F}
\end{tabular}\\
How many boxes did Shop C sell?

\task The pictogram shows students in after-school groups. Key: \picto{1}{S} = 2 students.\\[0.3em]
\begin{tabular}{ll}
Coding & \picto{6}{S} \\
Chess  & \picto{4}{S} \\
Art    & \picto{5}{S}
\end{tabular}\\
How many students are in Coding and Chess altogether?

\task A pie chart shows a survey of 200 people. If 35\% chose pizza, how many people is that?

\task A pictogram uses 1 symbol to represent 5 apples. If a row has 7 symbols, how many apples does it represent?

\end{tasks}

\end{document}
