\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Analysing time series graphs - TSN — Excellence}}
\begin{tasks}(3)
\task Analyse this scenario: A café's daily sales show overall growth, weekly patterns (busier weekends), and a spike when a celebrity visited. Identify and justify T, S, N.
\task A time series shows decreasing trend with strong annual seasonality. How would removing the seasonality affect appearance of the trend?
\task Compare the usefulness of T, S, and N for: a) forecasting, b) understanding causes, c) identifying problems.
\task Design a time series with: increasing trend, quarterly seasonality, and one noise event. Describe what each component represents.
\task A business sees sales increase Jan-Mar, drop Apr-Jun, repeat yearly. Is this trend or seasonality? Justify.
\task How can noise be distinguished from the start of a new trend?
\task Critique: "This time series has a positive trend because it goes up and down." What's wrong?
\task Given monthly temperature data for 5 years, describe how you'd identify T, S, and N.
\task Why might a time series appear to have no trend when it actually has seasonality masking it?
\task A dataset has both weekly and yearly seasonality. How would this appear in a time series graph?
\task Explain how TSN analysis could help a farmer plan crop planting and harvesting.
\task If noise is removed from data before analysis, what potential information might be lost?
\task Compare TSN analysis for: a) stock prices, b) website traffic, c) climate data. How do components differ?
\task Propose a real-world situation where identifying noise is more important than identifying trend.
\end{tasks}

\end{document}