\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Analysing time series graphs - TSN — Foundation}}
\begin{tasks}(3)
\task What does TSN stand for when analysing time series graphs?
\task In TSN, what does the T stand for?
\task In TSN, what does the S stand for?
\task In TSN, what does the N stand for?
\task What are the two possible long-term trends (T) in a time series?
\task What is seasonality (S) in a time series graph?
\task What is noise (N) in a time series graph?
\task True or false: A long-term trend can be described as "positive" or "negative".
\task True or false: Seasonality refers to regular patterns that repeat over time.
\task True or false: Noise refers to the main pattern in the data.
\task Which TSN component would describe a general increase in sales over 5 years?
\task Which TSN component would describe higher ice cream sales every summer?
\task Which TSN component would describe an unexpected drop in sales due to a one-time event?
\task Circle the correct description: Long-term trend shows the overall direction / seasonal patterns / unusual points.
\end{tasks}

\end{document}