\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Analysing time series graphs - TSN — Proficient}}
\begin{tasks}(3)
\task A company's profits show a general increase from 2015 to 2020, with higher profits every Q4. Identify T, S, and N.
\task Temperature data shows a slight decrease over 10 years, with peaks every July and troughs every January. Identify T, S, and N.
\task A time series has an increasing trend with regular peaks every 3 months. What components are present?
\task Describe what T, S, and N would look like in a graph of monthly electricity usage.
\task A retail store has increasing sales trend with Christmas spikes. One year had a fire closure. Identify all TSN components.
\task Why is it wrong to say a trend is "positive" or "negative"?
\task Give an example of seasonality in: a) retail sales, b) tourism, c) agriculture.
\task What might cause noise in: a) website traffic data, b) stock prices, c) temperature records?
\task A time series shows decreasing trend with no regular patterns but has one very high point. What could explain the high point?
\task Compare two time series: Series A has clear seasonality, Series B has no seasonality. What does this tell you?
\task If you remove the noise from a time series, what are you left with?
\task How can identifying seasonality help a business with planning?
\task A time series has an increasing trend with quarterly seasonality. Sketch what this might look like.
\task True or false: All time series have all three TSN components.
\end{tasks}

\end{document}