\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

{\LARGE \textbf{Selecting appropriate displays --- Excellence}}
\begin{tasks}(3)
\task A student uses a pie chart to show the temperature at midday for \mbox{$7$} days. Explain why that is a poor choice.
\task A student uses a line graph for favourite movie genres. Explain why that is a poor choice.
\task A researcher has exact jump heights for \mbox{$18$} athletes. Which display would you choose, and why?
\task A researcher has jump heights grouped into \mbox{$5$} cm intervals. Which display would you choose, and why?
\task A principal wants one display that compares the median and interquartile range of test scores for two classes. Which display is best, and why?
\task A student says a bar graph and a histogram are basically the same. Give one reason why that is wrong.
\task Which display is best for showing how petrol price changes each week across a term? Explain.
\task Which display is best for showing the proportion of students in each house group? Explain.
\task Which display is best for showing the distribution of travel times to school when the times are grouped into intervals? Explain.
\task Which display is best for showing the exact number of books read by each student in a small class? Explain.
\task A teacher wants to compare the spread of heights for Year \mbox{$9$} and Year \mbox{$10$} using one display. Which display is best, and why?
\task A student chooses a pie chart for grouped exam-score intervals because there are categories. What is the better display, and why?
\task A weather report wants to show rainfall each month over three years. Which display is best, and why?
\task A dot plot and a histogram can both be used for numerical data. Give one situation where the dot plot is the better choice.
\task Give one situation where a histogram is better than a dot plot.
\task Choose the best display for each case and justify briefly: favourite colour, pulse rate every minute, and masses grouped into intervals.
\end{tasks}

\end{document}
