\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Selecting appropriate displays --- Foundation}}
\begin{tasks}(3)
\task Choose the best display for favourite pizza toppings: bar graph or line graph.
\task Choose the best display for rainfall each month through a year: line graph or pie chart.
\task Choose the best display for shoe sizes in one class: dot plot or time series.
\task Choose the best display for colours of cars in a car park: pie chart or histogram.
\task Choose the best display for test marks grouped into score intervals: histogram or pie chart.
\task Choose the best display for a plant height measured every week: line graph or bar graph.
\task Choose the best display for the number of pets owned by each student: dot plot or time series.
\task Choose the best display for ways students travel to school: bar graph or line graph.
\task Choose the best display for lengths of fish grouped into \mbox{$5$} cm intervals: histogram or bar graph.
\task Choose the best display for temperature at \mbox{$9$} am each day for two weeks: line graph or pie chart.
\task Which display best shows parts of a whole: pie chart or dot plot?
\task Which display best shows change over time: line graph or pie chart?
\task Which display best shows individual small whole-number values: dot plot or histogram?
\task Which display best shows grouped continuous data: histogram or bar graph?
\end{tasks}

\end{document}
