\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Selecting appropriate displays --- Proficient}}
\begin{tasks}(3)
\task A class records daily attendance for \mbox{$20$} school days. Which display is best, and why?
\task A survey asks students for their favourite sport. Which display is best for showing the frequencies, and why?
\task A group records the masses of apples and sorts them into \mbox{$20$} g intervals. Which display is best, and why?
\task A student records how many goals their team scored in each match this season. Which display is best, and why?
\task A clinic compares the waiting times of two groups and wants to show median and spread. Which display is best, and why?
\task A class records the number of siblings each student has. Which display is better: dot plot or pie chart? Explain.
\task A scientist measures the temperature of water every minute for half an hour. Which display is best, and why?
\task A shop groups customer ages into \mbox{$10$}-year intervals. Which display is better: histogram or bar graph? Explain.
\task A student wants to show what fraction of the class chose each lunch option. Which display is best, and why?
\task A coach wants to compare the heights of two teams in one display. Which display is best, and why?
\task A teacher writes the exact quiz scores out of \mbox{$10$} for each student. Which display is better: dot plot or histogram? Explain.
\task A report shows the number of library books borrowed each month. Which display is better: line graph or pie chart? Explain.
\end{tasks}

\end{document}
