\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Volume of cubes and cuboids — Excellence}}
\begin{tasks}(3)
\task A cube has side length \mbox{$x$} cm. Write an expression for its volume.
\task A cuboid has length \mbox{$l$} cm, width \mbox{$w$} cm, and height \mbox{$h$} cm. Write an expression for its volume.
\task If a cube's side length doubles, what happens to its volume? Explain.
\task If all dimensions of a cuboid triple, what happens to its volume? Explain.
\task A cube has volume 216 cm\mbox{$^3$}. Find its side length.
\task A cuboid has volume 360 cm\mbox{$^3$}. Its length is 12 cm and width is 5 cm. Find its height.
\task Convert 3.75 m\mbox{$^3$} to cm\mbox{$^3$}.
\task Convert 8,500,000 mm\mbox{$^3$} to m\mbox{$^3$}.
\task A swimming pool is 25 m long, 10 m wide, and has an average depth of 1.5 m. What is its volume in cubic metres? In litres? (1 m\mbox{$^3$} = 1000 L)
\task A cube and a cuboid have equal volume. The cube has side 10 cm. The cuboid has length 20 cm and width 5 cm. Find the cuboid's height.
\task Which has greater volume and by how much: a 15 cm cube or a cuboid 18 cm × 12 cm × 8 cm?
\task A room is 6 m long, 4.5 m wide, and 2.8 m high. What is its volume? If paint covers 12 m\mbox{$^2$} per litre, how many litres are needed for the walls (excluding floor and ceiling)?
\task A box measures 1.2 m × 0.8 m × 0.6 m. How many cubes of side 20 cm can fit inside?
\task A storage container has volume 48 m\mbox{$^3$}. If its length is 6 m and height is 2 m, find its width.
\task A cube's volume is 64 times larger than another cube. How many times longer is its side?
\task Explain why volume is measured in cubic units, not square units.
\task A cuboid's length is twice its width, and its height is three times its width. If its volume is 150 cm\mbox{$^3$}, find its dimensions.
\task A cube of side 4 cm is cut into smaller cubes of side 1 cm. How many small cubes are produced?
\task Water flows into a tank at 2 litres per second. The tank is a cuboid 1 m × 0.8 m × 0.5 m. How long will it take to fill?
\task A rectangular prism has volume \mbox{$V$}, length \mbox{$l$}, width \mbox{$w$}, and height \mbox{$h$}. Rearrange \mbox{$V = lwh$} to make \mbox{$h$} the subject.
\task A company makes boxes in two sizes: small (10 cm × 8 cm × 6 cm) and large (15 cm × 12 cm × 10 cm). What is the ratio of their volumes?
\task A cube has surface area 150 cm\mbox{$^2$}. Can you find its volume? Explain your reasoning.
\task A cuboid has a square base of side 5 cm. Its volume is 200 cm\mbox{$^3$}. Find its height.
\task If you double the length and halve the width of a cuboid while keeping height constant, what happens to the volume?
\task A room's length, width, and height are in the ratio 3:2:1. If its volume is 192 m\mbox{$^3$}, find its dimensions.
\end{tasks}

\end{document}