\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Sampling methodology --- Foundation}}
\begin{tasks}(3)
\task Which sampling method gives every person in the population an equal chance of being chosen?
\task A teacher asks the first \mbox{$10$} students who walk into class. Is this random sampling?
\task A survey is posted on one gaming website. Does this give a fair sample of all teenagers? Why not?
\task Match the method to the description: random, systematic, or convenience. Taking every \mbox{$5$}th name on a list is \rule{2.4cm}{0.4pt} sampling.
\task Taking the easiest people to ask is called \rule{2.8cm}{0.4pt} sampling.
\task Choosing names from a hat is an example of \rule{2.4cm}{0.4pt} sampling.
\task A school wants student opinions from all year levels. Why might asking only Year \mbox{$9$} students be unfair?
\task A population has \mbox{$60\%$} girls and \mbox{$40\%$} boys. Which method tries to keep those same proportions in the sample?
\task In systematic sampling, if you start at the \mbox{$3$}rd name and take every \mbox{$4$}th name, what is the next name chosen after \mbox{$3$}?
\task A sample only includes students from the football team. Is this likely to be biased?
\task Why is a larger sample usually better than a very small sample?
\task A researcher wants to know favourite lunch food in the whole school. Give one place where surveying only there could cause bias.
\task If a survey only includes people who choose to reply, what problem might this create?
\task Write one reason why stratified sampling can be fairer than convenience sampling.
\end{tasks}

\end{document}
