\documentclass[17pt,a4paper,landscape]{extarticle}
\usepackage[margin=2.35cm,top=0.12cm,left=1.05cm]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{tasks}
\usepackage{tikz}
\usepackage{xcolor}
\usepackage[sfdefault,lf]{FiraSans}
\renewcommand{\familydefault}{\sfdefault}
\setlength{\parindent}{0pt}
\pagestyle{empty}
\settasks{label=\textbf{\arabic*.}, label-width=2.2em, item-indent=2.95em, column-sep=2.1cm, after-item-skip=4.7em}
\renewcommand{\arraystretch}{1.15}
\everymath{\displaystyle}

\begin{document}
\sffamily
\boldmath

\boldmath

\boldmath

{\LARGE \textbf{Sampling methodology --- Proficient}}
\begin{tasks}(3)
\task Compare these methods for a canteen survey: the first \mbox{$20$} students seen at lunch, or \mbox{$20$} names chosen randomly from the roll.
\task A list has students numbered \mbox{$1$} to \mbox{$120$}. Start at \mbox{$4$} and take every \mbox{$10$}th student. Write the first four numbers chosen.
\task A town survey wants each age group represented in the same proportions as the population. Which sampling method suits this best?
\task A survey about bus travel is taken only at a bus stop. Explain the bias.
\task Convenience sampling is fast. Give one advantage and one disadvantage.
\task A school has \mbox{$500$} juniors and \mbox{$300$} seniors. For a stratified sample of \mbox{$40$}, how many juniors and seniors should be chosen?
\task A class surveys homework time using volunteers only. Why could this be biased?
\task A researcher chooses every \mbox{$8$}th customer entering a store. Name this method and give one way it could still be unfair.
\task Why can one simple random sample give a different result from another?
\task A population has city and rural households, but the sample has only city households. What is wrong with the methodology?
\task Give one situation where stratified sampling is better than simple random sampling.
\task Why can a well-chosen sample of \mbox{$200$} be more trustworthy than a badly chosen sample of \mbox{$500$}?
\end{tasks}

\end{document}
